---
title: "exercise_2"
output: html_document
date: "2024-07-23"
---

The following exercise will help you understand the challenges of a matching model. 

 You can first run all the code and read the different informations about the result graphics. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r pressure, echo=FALSE}
# script to manualy adjust bins of CEM matching

# load/install packages if necessary
lop <- c("ggplot2", "tidyr", "dplyr", "tidyverse", "sf", "MatchIt", "fixest", "cobalt", "ggpubr", "basemaps", "reshape2", "scales")
newp <- lop[!(lop %in% installed.packages()[,"Package"])]
if(length(newp)) install.packages(newp)
lapply(lop, require, character.only = TRUE)
```


# Settings

```{r pressure, echo=FALSE}
# Define the path to a working directory where output will be saved
wdir = file.path("/datadrive/melvin/mapme.protectedareas/paIE_useCase/data_output/500ha")
# Define path for output (matched dataset)
path_matched = file.path(wdir, "matched_frame_adj")
# Define path for output cem statistics
path_cemstats = file.path(wdir, "cem_statistics_adj")
# Define path for output cem statistics
path_cemplots = file.path(wdir, "cem_plots_adj")



# project info 
bmz <- as.character(200466458)       
wdpaid.target <- 20011           

# Define the file name of the input matching frame
name_mf = "mf_BOL_500ha.gpkg"
mf.file = file.path(wdir, name_mf) 
###optional settings###
# Define the file name of the output matched dataset
name_matched = paste0("cem_tn_matched_data_", bmz, "_", as.character(wdpaid.target), ".gpkg")

# Column Names of Covariates in the Matching Frame
colname.travelTime = "travelTime_median_min_5k_110mio"
colname.clayContent = "clay_0.5cm_mean_gPer100g"
colname.elevation = "elevation_mean_m"
colname.tri = "tri_mean_m"
colname.fcIni = "fc_percent_2000"
colname.flprefund = "avgLoss_prefund"

# Prefix of columns for forest cover
colfc.prefix = "fc"
# Separation between prefix and year
colfc.bind = "_"
# Prefix of columns for forest loss
colfl.prefix = "fl"
```


```{r pressure, echo=FALSE}
###=======================CEM Matching=======================================###
# Load matching frame
mf = st_read(mf.file) %>%
  filter(group==0 | group==1) %>%
  filter(wdpaid==0 | wdpaid == wdpaid.target) %>%
  drop_na() %>%
  mutate(centroids = st_centroid(geom), 
         lat = st_coordinates(centroids)[,2],
         lon = st_coordinates(centroids)[,1]) %>%
  select(-centroids)

# Year of funding start
#funding.start = unique(mf$first_year)
funding.start = 2007

# Split geometry attribute
df.geom = mf[, c("assetid", "geom")] %>% as.data.frame()
# Drop geometry from matching frame
mf = mf %>% st_drop_geometry()

# Columns treeloss 2001 ~ 2009, without geometry
t = funding.start-2001
forestloss_prefund = mf[grepl(colfl.prefix, names(mf))][1:t] #%>% st_drop_geometry()
# Add column: average treeloss before funding starts,
mf$avgLoss_prefund = abs(round(rowMeans(forestloss_prefund), 2))
rm(forestloss_prefund)
# Column Name for average forest loss pre funding
colname.flAvg = colname.flprefund

# CEM with built-in cutoff method
# Create Formula from Variables
# Ref: https://stackoverflow.com/questions/66357664/using-variable-as-function-argument-in-r
formula = eval(bquote(group ~ .(as.name(colname.travelTime)) + .(as.name(colname.clayContent)) +
                        .(as.name(colname.elevation)) + .(as.name(colname.tri)) +
                        .(as.name(colname.fcIni)) + .(as.name(colname.flAvg))
))
```


```{r pressure, echo=FALSE}
# Make cut-off list ####
lst_cutoffs = c()

# Cut off the value distribution of individual covariates by quantile,
# And aggregate the threshold values to a list
lst_cutoffs[[colname.travelTime]] = as.integer(quantile(mf[[colname.travelTime]], probs = seq(0, 1, 0.1), na.rm=TRUE))

lst_cutoffs[[colname.clayContent]] = as.integer(quantile(mf[[colname.clayContent]], probs = seq(0, 1, 0.2), na.rm=TRUE))
#lst_cutoffs[[colname.clayContent]] = as.integer(c(0,10,20,30, 32,34,36,38,40, 50,60,70,80,90,100))

lst_cutoffs[[colname.elevation]] = as.integer(quantile(mf[[colname.elevation]], probs = seq(0, 1, 0.01), na.rm=TRUE))
#lst_cutoffs[[colname.elevation]] =  (c(0,200,750,2000,4000,6000))

lst_cutoffs[[colname.tri]] = as.integer(quantile(mf[[colname.tri]], probs = seq(0, 1, 0.1), na.rm=TRUE))

lst_cutoffs[[colname.fcIni]] = as.integer(quantile(mf[[colname.fcIni]], probs = seq(0, 1, 0.25), na.rm=TRUE))

lst_cutoffs[[colname.flprefund]] = (quantile(mf[[colname.flprefund]], probs = seq(0, 1, 0.33), na.rm=TRUE))
#lst_cutoffs[[colname.flprefund]] =  (c(0,0.01,0.03,0.12,1))



# CEM Match
out.cem = matchit(formula,
                  data = mf, 
                  method = "cem", 
                  cutpoints = lst_cutoffs)
summary(out.cem)
```


4. Generate CEM Statistics
```{r pressure, echo=FALSE}
# Save CEM Statistics to Dataframe
# Summary of matching output
cem.stats = summary(out.cem)
# Transform labelled matrix to dataframe
df.stats.1 = data.frame(covar = rownames(cem.stats$sum.matched),
                        cem.stats$sum.matched,
                        stringsAsFactors = FALSE)
# Simplify labels for covariates
df.stats.1[colname.travelTime,]$covar = "travelTime"
df.stats.1[colname.clayContent,]$covar = "clayContent"
df.stats.1[colname.elevation,]$covar = "elevation"
df.stats.1[colname.tri,]$covar = "tri"
df.stats.1[colname.fcIni,]$covar = "fc2000"
df.stats.1[colname.flAvg,]$covar = "flb4fund"
# Remove row names
rownames(df.stats.1) = NULL
# Reshape dataframe to single-row dataframe, relabel columns, add wdpaid as column
df.stats.1 = dcast(melt(df.stats.1, id.var="covar"), wdpaid.target~variable+covar)

# Repeat the above for statistics of CEM counts
df.stats.2 = data.frame(covar = rownames(cem.stats$nn),
                        cem.stats$nn,
                        stringsAsFactors = FALSE)
rownames(df.stats.2) = NULL
# Reshape dataframe to single-row dataframe, relabel columns, add bmzNo. as column
df.stats.2 = dcast(melt(df.stats.2, id.var="covar"), bmz~variable+covar)

# Merge both CEM statistics CEM
df.stats = cbind(df.stats.2, df.stats.1)
# Export CEM statistics
write.csv(df.stats,
          file = file.path(path_cemstats, paste0("cemstats_bmz_",bmz, "_wdpa_", as.character(wdpaid.target),".csv")),
          #sep = ",",
          row.names = FALSE)

###==================Matched Data============================================###
# Convert dataframe of matched objects to pivot wide form
matched.wide.1 = match.data(object=out.cem, data=mf) %>%
  # Add column "matched", mark matched observations as 1
  mutate(matched = 1)


# Export matched dataset
st_write(matched.wide.1,
         dsn = file.path(path_matched, paste0("cem_tn_matched_data_", bmz, "_", as.character(wdpaid.target), ".gpkg")),
         delete_dsn = TRUE)
```


[Info on balance plot]




```{r pressure, echo=FALSE}
#==========================Balance Plot====================================
# Define Covariate Labels to show on plots
c_name = data.frame(old = c(colname.travelTime, colname.clayContent, colname.elevation, colname.tri, colname.fcIni, colname.flAvg),
                    new = c("Accessibility", "Clay Content", "Elevation",
                            "TRI", "Forest Cover in 2000", paste0("avg. Annual Forest \n Loss 2007~", as.character(funding.start-1))))

# Refer to cobalt::love.plot()
# https://cloud.r-project.org/web/packages/cobalt/vignettes/cobalt.html#love.plot
p_covBal = love.plot(out.cem,
                     binary = "std",
                     abs = TRUE,
                     #thresholds = c(m = .1),
                     var.order = "unadjusted",
                     var.names = c_name,
                     sample.names = c("All Samples", "Selected Samples"),
                     wrap = 15) # at how many characters does axis label break to new line

# Finetune Layouts using ggplot
# Reference for log-scales ticks:
# https://www.datanovia.com/en/blog/ggplot-log-scale-transformation/#set-axis-into-log2-scale
p_covBal <- p_covBal +
  # Log-transform X-axis
  #scale_x_log10(breaks = scales::trans_breaks("log10", function(x) 10^x),
  #              labels = scales::trans_format("log10", scales::math_format(10^.x)))+
  geom_vline(aes(xintercept=0.2,
                 linetype="Good Balance \n (0<=x<=0.2)"),
             color=c("#2ecc71"), linewidth=0.35) +
  labs(x = "Absolute Standarized Mean Differrence \n between Treated and Control Group") +
  theme_bw() +
  theme(
    plot.title = element_text(family="Arial Black", size=16, hjust=0.5),
    
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text=element_text(size=14),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    
    axis.text.x = element_text(angle = 20, hjust = 0.5, vjust = 0.5),
    axis.text=element_text(size=12),
    axis.title=element_text(size=14),
    axis.title.y = element_text(margin = margin(unit = 'cm', r = 0.5)),
    axis.title.x = element_text(margin = margin(unit = 'cm', t = 0.5)),
    
    panel.grid.major.x = element_line(color = 'grey', linewidth = 0.3, linetype = 1),
    panel.grid.minor.x = element_line(color = 'grey', linewidth = 0.3, linetype = 2)
  ) + guides(linetype = guide_legend(override.aes = list(color = "#2ecc71"))) # Add legend for geom_vline

p_covBal %>% ggexport(filename = file.path(path_cemplots, "covBal", paste0("cem_tn_covBal_", bmz, "_", as.character(wdpaid.target), ".png")))
```



[Info on histogramms]

```{r pressure, echo=FALSE}
#==========================Histogramms========================
# Convert dataframe of matched objects to pivot wide form
matched.wide.1 = match.data(object=out.cem, data=mf) %>%
  # Add column "matched", mark matched observations as 1
  mutate(matched = 1)

# Subset to unmatched treatment
unmatched.treat = mf %>%
  filter(group == 1) %>%
  filter(!assetid %in% matched.wide.1$assetid) %>%
  mutate(matched = 0)

# Add dropped Treatment back to the matched dataset
matched.wide.2 = bind_rows(matched.wide.1, unmatched.treat) %>%
  # Add geometry
  left_join(., df.geom, by="assetid")

matched.wide.3 = matched.wide.2 %>%
  mutate(group = replace(group, group==1, "Treatment")) %>%
  mutate(group = replace(group, group==0, "Control"))

# Define Facet Labels
fnl = c(`Unadjusted Sample` = "Before Matching",
        `Adjusted Sample` = "After Matching")

size.axis.label = 8
size.axis.title = 9
size.legend.label = 9
size.facet.label = 9

# Density plot for Travel Time
p_travel = bal.plot(out.cem,
                    var.name = colname.travelTime,
                    which = "both") +
  facet_wrap(.~which, labeller = as_labeller(fnl)) +
  scale_fill_manual(labels = c("Control", "Treatment"), values = c("#f5b041","#5dade2")) +
  labs(#title = "Distributional Balance for Accessibility",
    x = "Accessibility (min)",
    fill = "Group") +
  theme_bw() +
  theme(
    plot.title = element_blank(),
    
    legend.title = element_blank(),
    legend.text=element_text(size=size.legend.label),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    
    axis.text=element_text(size=size.axis.label, angle = 20, hjust = 0.7, vjust = 0.7),
    axis.title=element_text(size=size.axis.title),
    
    # Facet Label
    strip.text.x = element_text(size = size.facet.label))


p_clay = bal.plot(out.cem,
                  var.name = colname.clayContent,
                  which = "both") +
  facet_wrap(.~which, labeller = as_labeller(fnl)) +
  scale_fill_manual(labels = c("Control", "Treatment"), values = c("#f5b041","#5dade2")) +
  labs(#title = "Distributional Balance for Clay Content",
    x = "Clay Content \n (0~20cm, %)",
    fill = "Group") +
  theme_bw() +
  theme(
    plot.title = element_blank(),
    
    legend.title = element_blank(),
    legend.text=element_text(size=size.legend.label),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    
    axis.text=element_text(size=size.axis.label, angle = 20, hjust = 0.7, vjust = 0.7),
    axis.title=element_text(size=size.axis.title),
    
    # Facet Label
    strip.text.x = element_text(size = size.facet.label))


p_elevation = bal.plot(out.cem,
                       var.name = colname.elevation,
                       which = "both") +
  facet_wrap(.~which, labeller = as_labeller(fnl)) +
  scale_fill_manual(labels = c("Control", "Treatment"), values = c("#f5b041","#5dade2")) +
  labs(#title = "Distributional Balance for Elevation",
    x = "Elevation (m)",
    fill = "Group") +
  theme_bw() +
  theme(
    plot.title = element_blank(),
    
    legend.title = element_blank(),
    legend.text=element_text(size=size.legend.label),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    
    axis.text=element_text(size=size.axis.label, angle = 20, hjust = 0.7, vjust = 0.7),
    axis.title=element_text(size=size.axis.title),
    
    # Facet Label
    strip.text.x = element_text(size = size.facet.label))


p_tri = bal.plot(out.cem,
                 var.name = colname.tri,
                 which = "both") +
  facet_wrap(.~which, labeller = as_labeller(fnl)) +
  scale_fill_manual(labels = c("Control", "Treatment"), values = c("#f5b041","#5dade2")) +
  labs(#title = "Distributional Balance for TRI",
    x = "TRI",
    fill = "Group") +
  theme_bw() +
  theme(
    plot.title = element_blank(),
    
    legend.title = element_blank(),
    legend.text=element_text(size=size.legend.label),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    
    axis.text=element_text(size=size.axis.label, angle = 20, hjust = 0.7, vjust = 0.7),
    axis.title=element_text(size=size.axis.title),
    
    # Facet Label
    strip.text.x = element_text(size = size.facet.label))


p_fc = bal.plot(out.cem,
                var.name = colname.fcIni,
                which = "both") +
  facet_wrap(.~which, labeller = as_labeller(fnl)) +
  scale_fill_manual(labels = c("Control", "Treatment"), values = c("#f5b041","#5dade2")) +
  labs(#title = "Distributional Balance for \n Forest Cover in 2000",
    x = "Forest Cover (%)",
    fill = "Group") +
  theme_bw() +
  theme(
    plot.title = element_blank(),
    
    legend.title = element_blank(),
    legend.text=element_text(size=size.legend.label),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    
    axis.text=element_text(size=size.axis.label, angle = 20, hjust = 0.7, vjust = 0.7),
    axis.title=element_text(size=size.axis.title),
    
    # Facet Label
    strip.text.x = element_text(size = size.facet.label))


p_fl = bal.plot(out.cem,
                var.name = colname.flAvg,
                which = "both") +
  facet_wrap(.~which, labeller = as_labeller(fnl)) +
  scale_fill_manual(labels = c("Control", "Treatment"), values = c("#f5b041","#5dade2")) +
  labs(#title = paste0("Distributional Balance for \n avg. Forest Loss 2001~", as.character(funding.start-1)),
    x = "avg.Forest Loss pre-funding (%)",
    fill = "Group") +
  theme_bw() +
  theme(
    plot.title = element_blank(),
    
    legend.title = element_blank(),
    legend.text=element_text(size=size.legend.label),
    legend.spacing.x = unit(0.5, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    legend.position = "none",
    
    axis.text=element_text(size=size.axis.label, angle = 20, hjust = 0.7, vjust = 0.7),
    axis.title=element_text(size=size.axis.title),
    
    # Facet Label
    strip.text.x = element_text(size = size.facet.label))

p_density = ggpubr::ggarrange(p_fc, p_fl, p_elevation, p_tri, p_clay, p_travel,
                              ncol=2, nrow = 3,
                              #labels=c("A","B"),
                              common.legend = TRUE,
                              legend = "bottom")
p_density %>% ggexport(filename = file.path(path_cemplots, "density", paste0("cem_tn_density_", bmz, "_", as.character(wdpaid.target), ".png")))
```


[Info on trend plot]

```{r pressure, echo=FALSE}
#=========================Trend Plot================================
# Pivot Wide ==> Pivot Long
matched.long = matched.wide.1 %>%
  st_drop_geometry() %>%
  select(c(group, wdpaid, assetid, weights, starts_with(colfc.prefix))) %>%
  pivot_longer(cols = c(starts_with(colfc.prefix)),
               names_to = c("var1", "var2", "year"),
               names_sep = colfc.bind,
               values_to = "fc_pct") %>%
  # Round forest cover percentage > 100% (due to processing bias in pre-processing) to 100%
  mutate(fc_pct = ifelse(fc_pct>100, plyr::round_any(fc_pct,10), fc_pct))

# Pivot Wide ==> Pivot Long
unmatched.long = mf %>%
  st_drop_geometry() %>%
  select(c(group, wdpaid, assetid, starts_with(colfc.prefix))) %>%
  pivot_longer(cols = c(starts_with(colfc.prefix)),
               names_to = c("var1", "var2", "year"),
               names_sep = colfc.bind,
               values_to = "fc_pct") %>%
  # Round forest cover percentage > 100% (due to processing bias in pre-processing) to 100%
  mutate(fc_pct = ifelse(fc_pct>100, plyr::round_any(fc_pct,10), fc_pct))

# Make dataframe for plotting Trend
df.matched.trend = matched.long %>%
  group_by(group, year) %>%
  summarise(avgFC = mean(fc_pct, na.rm=TRUE), n = n(), matched = TRUE)

df.unmatched.trend = unmatched.long %>%
  group_by(group, year) %>%
  summarise(avgFC = mean(fc_pct, na.rm=TRUE), n = n(), matched = FALSE)

df.trend = rbind(df.matched.trend, df.unmatched.trend)

# Change Facet Labels
fct.labs <- c("Before Matching", "After Matching")
names(fct.labs) <- c(FALSE, TRUE)

# Trend Plot
trend.plot <- ggplot(df.trend, aes(x = year, y = avgFC)) +
  geom_line(aes(group = group, color = as.character(group))) +
  geom_point(aes(color = as.character(group))) +
  geom_vline(aes(xintercept=as.character(funding.start), size="Funding Start"), linetype=2, linewidth=0.5, color="orange") +
  
  scale_x_discrete(breaks=seq(2000,2020,5), labels=paste(seq(2000,2020,5))) +
  scale_color_hue(labels = c("Control", "Treatment")) +
  
  facet_wrap(matched~., nrow = 1, #scales = 'free_x',
             labeller = labeller(matched = fct.labs)) +
  
  labs(x = "Year", y = "Average Forest Cover (%) per 500ha square", color = "Group") +
  theme_bw() +
  theme(
    axis.text.x = element_text(angle = -20, hjust = 0.5, vjust = 0.5),
    axis.text=element_text(size=11),
    axis.title=element_text(size=14),
    
    legend.position = "bottom",
    legend.title = element_blank(),
    legend.text=element_text(size=14),
    #legend.spacing.x = unit(1.0, 'cm'),
    legend.spacing.y = unit(0.75, 'cm'),
    legend.key.size = unit(2, 'line'),
    
    panel.grid.major.x = element_line(color = 'grey', linewidth = 0.3, linetype = 1),
    panel.grid.minor.x = element_line(color = 'grey', linewidth = 0.2, linetype = 2),
    panel.grid.major.y = element_line(color = 'grey', linewidth = 0.3, linetype = 1),
    panel.grid.minor.y = element_line(color = 'grey', linewidth = 0.2, linetype = 2),
    
    strip.text.x = element_text(size = 12) # Facet Label
  ) + guides(size = guide_legend(override.aes = list(color = "orange"))) # Add legend for geom_vline

trend.plot %>% ggexport(filename = file.path(path_cemplots, "trend", paste0("cem_tn_trend_", bmz, "_", as.character(wdpaid.target), ".png")))
```


Q1: Observe and describe the results focusing both on the quality of the matching and the quantity of units matched. 

- How many cells are successfully matched ? 
- Describe the balance of treatment and control groups 


#Part II / Maximizing Quantity 
Q2: Change the size of the bins used for the matching. 

[paste the same code ]

