---
title: "building_projects_WDPA"
author: "Antoine Vuillot"
date: "06/06/2023"
output: html  
---

OUTDATED : THE PA DATABASE NEEDED TO BE COMPLETED WITH WDPA ID. IT WAS DONE MANUALLY BY INGRID AND LEA. THE RAW DATABASE IS THEN BDD_JOINT (UP TO 2017). THE PART I OF LEA SCRIPT IS THUS UN-NECESSARY

# Create a database from SIOP extraction and AP database

In this script the project database extracted from the SIOP is merged with databases : on protected areas (PA hereafter) created by ARB, and on PAs around the world from WDPA. The cleaning and merging steps are described.

## Charging relevant packages

```{r}

library(tidyverse)
library(stargazer)
library(dplyr)
library(ggplot2)
library(RColorBrewer)
library(data.table)
library(readxl)
library(splitstackshape) 
```

## Importing databases
###SIOP

The extraction of the SIOP is imported, and the dataset widened from the cofunders ("cofinanciers"). Instead of having one row for a concours and a cofunder, we have one row with all cofunderS.

```{r}

#Importing the data extracted from SIOP
data_siop_raw = read_excel("C:/Users/vuillota/Desktop/projet_AiresProtegees/00_data_raw/AP_BO_2000-2017_V3.xlsx",
                           sheet = 1)

#Remove variables "Id. cofinancier","Libellé cofinancier" and widen the dataframe from "cofinancier"
data_siop_tidy = data_siop_raw %>%
  select(!c("Id. Cofinancier","Libellé cofinancier")) %>%
  pivot_wider(names_from = "Cofinancier", values_from ="Cofinancier") 

#DB Léa
data_siop_lea = data_siop_tidy

#Shorten with a list variabe of cofinancier ??

##The duplicated ID concorus : what to do with dem' ?
base_siop_dup = data_siop_tidy[duplicated(data_siop_tidy$ID_concours),]
  

```

###AP
The dataset for PAs as reported by ARB is imported. Some PAs are associated to several 

```{r}
#Importing data
data_AP_raw = read_excel("C:/Users/vuillota/Desktop/projet_AiresProtegees/00_data_raw/Basededonnees_AP.xlsx", 
                          sheet = 1)
#Keep relevant variables and create one line for each protected area
data_AP_tidy = data_AP_raw %>%
  #kep relevant variables and rename ID variables
  select(c("ID_concours","maitrise_ouvrage","surface(km2)","nb_AP","détail","projet","commentaires","ID_WDPA")) %>%
  rename("ID_WDPA_list" = "ID_WDPA") %>%
  #In the list of ID WDPA, keep ID only
  mutate(ID_WDPA = gsub("(\\D+)", ";", ID_WDPA_list)) %>%
  #Remove ";" character at the end
  mutate(ID_WDPA = gsub("[;.]$", "", ID_WDPA)) %>%
  #lengthen the dataset : one line corresponds to one ID_concours and one WDPA ID.
  #A ID_concours can be associated to more than one ID WDPA
  cSplit(splitCols = c('ID_WDPA'), ";", 
       direction = 'long',
       drop = FALSE,
       type.convert = FALSE) %>%
  #Convert ID WDPA to numeric
  mutate(ID_WDPA = as.numeric(ID_WDPA)) %>%
  #Finally adjust the ID_WDPA to specific cases : if "non existant" specified in WDPA_list, ID_WDPA set to NA
  mutate(ID_WDPA = ifelse(grepl("non existant", ID_WDPA_list, ignore.case = TRUE), yes = NA, no = ID_WDPA))

#DB Léa
data_AP_lea = data_AP_raw %>%
  #kep relevant variables and rename ID variables
  select(c("ID_concours","maitrise_ouvrage","surface(km2)","nb_AP","détail","projet","commentaires","ID_WDPA")) 
```

###WDPA

```{r}
# Import the WDPA database from IUCN
data_wdpa_raw = fread("C:/Users/vuillota/Desktop/projet_AiresProtegees/00_data_raw/WDPA_BDD.csv")

#Renaming, conversion of ID_WDPA to numeric and removing NA
#PAs with NA as ID_WDPA have no relevant information reported
data_wdpa_tidy = data_wdpa_raw %>%
  rename("ID_WDPA" = "WDPAID") %>%
  mutate(ID_WDPA = as.numeric(ID_WDPA)) %>%
  subset(is.na(ID_WDPA) == FALSE)

#DB Léa
data_wdpa_lea = data_wdpa_raw %>%
  rename("ID_WDPA" = "WDPAID")


```

##Merging databases

```{r}

#The databases are merged, and variables are modified
data_full = data_siop_tidy %>%
  left_join(data_AP_tidy, by = "ID_concours") %>%
  left_join(data_wdpa_tidy, by = "ID_WDPA") %>%
  #Change the format of numbers : get rid of XXX,00 which confuses the conversion
  mutate(across(.cols = c("Montant prévu concours (euro octroi)", "Mt global projet prévu (devise)",
                          "Engagements nets (euro octroi)", "montant_total_projet"),
                .fns = ~gsub("(,00)$", "", .x))) %>%
  #Convert from character to numeric
  mutate(across(.cols = c("Montant prévu concours (euro octroi)", "Mt global projet prévu (devise)",
                          "Engagements nets (euro octroi)", "montant_total_projet",  "Durée du concours (Année)",
                          "surface(km2)", "nb_AP", "WDPA_PID", "MARINE", "REP_M_AREA", 
                          "GIS_M_AREA", "REP_AREA", "GIS_AREA", "STATUS_YR", "METADATAID"),
                .fns = ~as.numeric(.x))) %>%
  #Change format of some variables (dates) from unknown to character
  mutate(across(.cols = c("Date_octroi", "Annee_octroi", "Dernier versement en date (projet)",
                          "Date signature convention (CF)"),
                .fns = ~as.character(.x))) %>%
  #Create the variable "Pays de réalisation v2" : equals "Pays de réalisation", but the rows with value "MULTIPAYS" take the value of "Autres pays de réalisation"
  mutate(`Pays de réalisation v2` = ifelse(`Pays de réalisation` == "MULTI-PAYS",
                                        yes = `Autres pays de réalisation`,
                                        no = `Pays de réalisation`),
         .after = "Pays de réalisation") %>%
  mutate(across(.cols = c("Pays de réalisation", "Pays de réalisation v2", 
                          "Direction_regionale", "Autres pays de réalisation"),
                .fns = ~tolower(.x))) %>%
  #Change IUC cat to its description
  mutate(iucn_des = case_when(
  !is.na(ID_WDPA) & IUCN_CAT == "Ia" ~ "Réserve naturelle intégrale",
  !is.na(ID_WDPA) & IUCN_CAT == "Ib" ~ "Zone de nature sauvage",
  !is.na(ID_WDPA) & IUCN_CAT == "II" ~ "Parc national",
  !is.na(ID_WDPA) & IUCN_CAT == "III" ~ "Monument naturel",
  !is.na(ID_WDPA) & IUCN_CAT == "IV" ~ "Gest. des habitats/espèces",
  !is.na(ID_WDPA) & IUCN_CAT == "V" ~ "Paysage protégé",
  !is.na(ID_WDPA) & IUCN_CAT == "VI" ~ "Gest. de ress. protégées",
  !is.na(ID_WDPA) & IUCN_CAT == "Not Applicable" ~ "Non catégorisée",
  !is.na(ID_WDPA) & IUCN_CAT == "Not Reported" ~ "Non catégorisée",
  !is.na(ID_WDPA) & IUCN_CAT == "Not Assigned" ~ "Non catégorisée",
  TRUE ~ "Non référencée"), .after = IUCN_CAT)

test = select(data_full, c("ID_concours", "IDPROJET", "ID_WDPA", "surface(km2)", "MARINE":"NO_TK_AREA"))

# test = data_AP_tidy %>%
#   left_join(data_siop_tidy, by = "ID_concours")

#Rep. Léa
data.joint = data_siop_lea %>% left_join(data_AP_lea, by = "ID_concours")
BDD_joint = left_join(data_full, data_wdpa_lea, by = "ID_WDPA")
#write.csv(BDD_joint, "C:/Users/vuillota/Desktop/BDD_joint.csv")

```

