---
title: "DesStat_PA_WDPA"
author: "Antoine Vuillot"
date: "12/06/2023"
output: 
  html_document: 
    fig_caption: yes
editor_options: 
  chunk_output_type: inline
---

# Descriptive statistics

In this document are performed and plotted descriptive statistics from the datasets built in buildingDB_PA_WDPA. The following statistics are derived :

-   Distribution of parcels among IUCN categories, at country, region and world level.
-   Distribution in terms of ecosystems
-   Distribution of PAs across countries and regions

## Importing packages

```{r setup, include=FALSE, eval = FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE, eval = FALSE}

library(tidyverse)
library(stargazer)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(data.table)
#library(readxl)
#library(splitstackshape) 
library(janitor)
library(xtable)
library(questionr)
library(tidyterra)
library(terra)
library(sf)
library(mapview)
library(aws.s3)
```

## Importing datasets

```{r, eval = FALSE}
#Both datasets are imported also in UTF8 encoding, for some variables
##A first dataset with some PA on more than one row (one line per funding for instance)
data_stat = 
  #fread("data_tidy/BDD_DesStat_nofund.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/BDD_DesStat_nofund.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

##A second dataset with one line per PA, more suited for some statistics
data_stat_nodupl = 
  #fread("data_tidy/BDD_DesStat_nofund_nodupl.csv" , encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/BDD_DesStat_nofund_nodupl.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_area_ctry = 
  #fread("data_tidy/area/pa_area_ctry.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_area_ctry.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_area_dr = 
  #fread("data_tidy/area/pa_area_dr.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_area_dr.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_area_wld = 
  #fread("data_tidy/area/pa_area_wld.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_area_wld.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_int_yr = 
  #fread("data_tidy/area/pa_area_dr.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_int_yr.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

```

## Performing descriptive statistics

### IUCN categories

#### Share of PAs by IUCN categories

```{r, eval = FALSE}

#Building the relevant dataset
##For all PAs ..
data_cat_iucn = data_stat_nodupl %>%
  group_by(iucn_des) %>%
  #number of PAs per IUCN category
  summarize(n_iucn = n()) %>%
  ungroup() %>%
  #Frequency of IUCN categories
  mutate(n_pa = sum(n_iucn),
         freq_iucn = round(n_iucn/n_pa*100, 1)) %>%
  arrange(desc(iucn_des)) %>%
  mutate(ypos_iucn = cumsum(freq_iucn) - 0.5*freq_iucn) 


##... and for referenced PAs only
data_cat_iucn_ref = data_stat_nodupl %>%
  #Remove not referenced PAs
  subset(!(iucn_des %in% c("Non catégorisée", "Non référencée"))) %>%
  group_by(iucn_des) %>%
  #number of PAs per IUCN category
  summarize(n_iucn = n()) %>%
  ungroup() %>%
  #Frequency of IUCN categories
  mutate(n_pa = sum(n_iucn),
         freq_iucn = round(n_iucn/n_pa*100, 1)) %>%
  arrange(freq_iucn) %>%
  mutate(ypos_iucn = cumsum(freq_iucn) - 0.5*freq_iucn) 

#Latex table
tbl_cat_iucn = data_cat_iucn %>%
  select(c(iucn_des, n_iucn, freq_iucn))
names(tbl_cat_iucn) <- c("Catégories IUCN","Nombre d'AP", "Proportion d'AP (%)")

tbl_cat_iucn_ref = data_cat_iucn_ref %>%
  select(c(iucn_des, n_iucn, freq_iucn))
names(tbl_cat_iucn_ref) <- c("Catégories IUCN","Nombre d'AP", "Proportion d'AP (%)")


#Histogram including non-referenced PAs
hist_cat_iucn = ggplot(data_cat_iucn, 
                       aes(x = reorder(iucn_des, -freq_iucn), 
                           y = freq_iucn, fill = iucn_des)) %>% 
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = round(n_iucn, 1), y = freq_iucn), 
            vjust = -0.1, color="black",
            size=3.5) %>%
  + labs(title = "Proportion d'aires protégées par catégorie IUCN",
         subtitle = paste("Echantillon :", sum(data_cat_iucn$n_iucn), "aires protégées. Nombre d'aires indiqué sur les barres."),
          x = "Catégories IUCN", 
          y = "Nombre (%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_cat_iucn

#Histogram excluding non-referenced PAs
hist_cat_iucn_ref = ggplot(data_cat_iucn_ref, 
                       aes(x = reorder(iucn_des, -freq_iucn), 
                           y = freq_iucn, fill = iucn_des)) %>% 
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = round(n_iucn, 1), y = freq_iucn), 
            vjust = -0.1, color="black",
            size=3.5) %>%
  + labs(title = "Proportion d'aires protégées par catégorie IUCN (hors AP non-répertoriées)",
         subtitle = paste("Echantillon :", sum(data_cat_iucn_ref$n_iucn), "aires protégées. Nombre d'aires indiqué sur les barres."),
          x = "Catégories IUCN", 
          y = "Nombre (%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_cat_iucn_ref


#Pie chart INcluding non-referenced PAs
pie_cat_iucn = ggplot(data_cat_iucn, 
                      aes(x="", y= freq_iucn, fill = iucn_des)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_iucn, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Proportion d'aires protégées par catégorie IUCN (%)",
         subtitle = paste("Echantillon :", sum(data_cat_iucn$n_iucn), "aires protégées")) %>%
  + scale_fill_brewer(name = "Catégories", palette = "Dark2") %>%
  + theme_void()
pie_cat_iucn



#Pie chart EXcluding non-referenced PAs
pie_cat_iucn_ref = ggplot(data_cat_iucn_ref, 
                      aes(x="", y= freq_iucn, fill = iucn_des)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_iucn, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Proportion d'aires protégées par catégorie IUCN \nhors aires non répertoriées (%)",
         subtitle = paste("Echantillon :", sum(data_cat_iucn_ref$n_iucn), "aires protégées")) %>%
  + scale_fill_brewer(name = "Catégories", palette = "Dark2") %>%
  + theme_void()
pie_cat_iucn_ref




```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "hist_cat_iucn.png", sep = "/"),
       plot = hist_cat_iucn,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "hist_cat_iucn_ref.png", sep = "/"),
       plot = hist_cat_iucn_ref,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "pie_cat_iucn.png", sep = "/"),
       plot = pie_cat_iucn,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "pie_cat_iucn_ref.png", sep = "/"),
       plot = pie_cat_iucn_ref,
       device = "png",
       height = 6, width = 9)

print(xtable(tbl_cat_iucn, type = "latex"),
      file = paste(tmp, "tbl_cat_iucn.tex", sep = "/"))

print(xtable(tbl_cat_iucn_ref, type = "latex"),
      file = paste(tmp, "tbl_cat_iucn_ref.tex", sep = "/"))

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/IUCN", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

#### IUCN categories by countries and regions

```{r, eval = FALSE}

#Build the distribution of IUCN categories at country level ...
data_iucn_ctry = table(data_stat_nodupl$iucn_des,
                       data_stat_nodupl$iso3) %>%
  #Create a table with all iucn categories for each country, and compute the frequencies in percent
  prop.table(2) %>%
  as.data.frame() %>%
  mutate(Freq = round(Freq, 3)*100) %>%
  pivot_wider(names_from = Var2, values_from = Freq) %>%
  rename("iucn_des" = "Var1")

#... and regional level
data_iucn_reg = table(data_stat_nodupl$iucn_des,
                       data_stat_nodupl$direction_regionale) %>%
    #Create a table with all iucn categories for each country, and compute the frequencies in percent
  prop.table(2) %>%
  as.data.frame() %>%
  mutate(Freq = round(Freq, 3)*100) %>%
  pivot_wider(names_from = Var2, values_from = Freq) %>%
  rename("iucn_des" = "Var1")

```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

print(xtable(data_iucn_ctry, type = "latex"),
      file = paste(tmp, "tbl_iucn_ctry.tex", sep = "/"))
print(xtable(data_iucn_reg, type = "latex"),
      file = paste(tmp, "tbl_iucn_reg.tex", sep = "/"))

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/IUCN", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

### Ecosystems (excluding non-referenced PAs)

#### Proportion of PAs by marine or terrestrial areas

```{r, eval = FALSE}

#Build datasets
data_eco = data_stat_nodupl %>%
  #subset non-referencded PAs (have NA ecosysteme)
  subset(is.na(marine) == FALSE) %>%
  mutate(marine = as.factor(marine))
data_eco$ecosyst_en = fct_recode(data_eco$marine, 
                              "Terrestrial"="0", 
                              "Coastal"="1", 
                              "Marine"="2")
data_eco$ecosyst_fr = fct_recode(data_eco$marine, 
                              "Terrestre"="0", 
                              "Côtier"="1", 
                              "Marin"="2")

data_eco_hist = data_eco %>%
  group_by(ecosyst_en, ecosyst_fr) %>%
  summarize(n = n(),
            freq = round(n/nrow(data_eco), 1)*100) %>%
  ungroup()

tbl_eco_world_fr = data_eco_hist %>%
  select(c(ecosyst_fr, n, freq)) %>%
  rename("Ecosystème" = "ecosyst_fr",
         "Nombre d'AP" = "n",
         "Proportion d'AP(%)" = "freq")

tbl_eco_world_en = data_eco_hist %>%
  select(c(ecosyst_en, n, freq)) %>%
  rename("Ecosystem" = "ecosyst_en",
         "Number of PAs" = "n",
         "Share of PAs(%)" = "freq")


#Histogram in share (in French)
hist_eco_shr_fr = ggplot(data_eco_hist, 
                     aes(x = ecosyst_fr, y = freq, fill = ecosyst_fr)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ geom_text(aes(label = round(n, 1), y = freq), 
        vjust = -0.1, color="black",
        size=3.5) %>%
+ labs(title = "Proportion d'aires protégées par type d'écosystème \n(hors AP non-référencées)",
       subtitle = paste("Echantillon :", sum(data_eco_hist$n), "aires protégées. Nombre d'aires indiqué sur les barres."),
         x = "Type d'écosystème",
         y = "Proportion d'aires protégées(%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 0,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_eco_shr_fr
# 



#Histogram in share (in English)
hist_eco_shr_en = ggplot(data_eco_hist, 
                     aes(x = ecosyst_en, y = freq, fill = ecosyst_en)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ geom_text(aes(label = round(n, 1), y = freq), 
        vjust = -0.1, color="black",
        size=3.5) %>%
+ labs(title = "Proportion of protected areas by ecosystem type \n(excluding non-references PAs)",
       subtitle = paste("Sample :", sum(data_eco_hist$n), "protected areas. Number of areas indicated above."),
         x = "Ecosystem type",
         y = "Proportion of protected areas(%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 0,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
#hist_eco_shr_en


  
#Histogram in number (in French)
hist_eco_n_fr = ggplot(data_eco_hist, 
                     aes(x = ecosyst_fr, y = n, fill = ecosyst_fr)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ labs(title = "Proportion d'aires protégées par type d'écosystème \n(hors AP non-référencées)",
       subtitle = paste("Echantillon :", sum(data_eco_hist$n), "aires protégées"),
         x = "Type d'écosystème",
         y = "Proportion d'aires protégées") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 0,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_eco_n_fr




#Histogram in number (in English)
hist_eco_n_en = ggplot(data_eco_hist, 
                     aes(x = ecosyst_en, y = n, fill = ecosyst_en)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ labs(title = "Proportion of protected areas by ecosystem type \n(excluding non-referenced PAs)",
       subtitle = paste("Sample :", sum(data_eco_hist$n), "protected areas"),
         x = "Ecosystem type",
         y = "Proportion of protected areas") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 0,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
#hist_eco_n_en

#Pie chart (in French)
pie_eco_fr = ggplot(data_eco_hist, 
                     aes(x = "", y = freq, fill = ecosyst_fr)) %>%
+ geom_bar(width = 1, stat = "identity",color="white") %>%
+ geom_label(aes(x=1.3, label = paste0(freq, "%")), 
             color = "black", position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
+ coord_polar("y", start=0) %>%
+ labs(title = "Proportion d'aires protégées par type d'écosystème \n(hors AP non-référencées)",
       subtitle = paste("Echantillon :", sum(data_eco_hist$n), "aires protégées"),
         x = "Type d'écosystème",
         y = "Proportion d'aires protégées") %>%
  + scale_fill_brewer(name = "Ecosystème", palette="Paired") %>%
  + theme_void()
#pie_eco_fr


#Histogram in number (in English)
pie_eco_en = ggplot(data_eco_hist, 
                     aes(x = "", y = n, fill = ecosyst_en)) %>%
+ geom_bar(width = 1, stat = "identity",color="white") %>%
+ geom_label(aes(x=1.3, label = paste0(freq, "%")), 
             color = "black", position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
+ coord_polar("y", start=0) %>%
+ labs(title = "Proportion of protected areas by ecosystem type \n(exluding non-referenced PAs)",
       subtitle = paste("Sample :", sum(data_eco_hist$n), "protected areas"),
         x = "Ecosystem type",
         y = "Proportion of protected areas") %>%
  + scale_fill_brewer(name = "Ecosystem", palette="Paired") %>%
  + theme_void()
pie_eco_en
  
```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")


ggsave(paste(tmp, "hist_eco_shr_fr.png", sep = "/"),
       plot = hist_eco_shr_fr,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "hist_eco_shr_en.png", sep = "/"),
       plot = hist_eco_shr_en,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "hist_eco_n_fr.png", sep = "/"),
       plot = hist_eco_n_fr,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "hist_eco_n_en.png", sep = "/"),
       plot = hist_eco_n_en,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "pie_eco_fr.png", sep = "/"),
       plot = pie_eco_fr,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "pie_eco_en.png", sep = "/"),
       plot = pie_eco_en,
       device = "png",
       height = 6, width = 9)

print(xtable(tbl_eco_world_fr, type = "latex"), 
      file = paste(tmp, "tbl_ecosyst_fr.tex", sep = "/"))
print(xtable(tbl_eco_world_en, type = "latex"), 
      file = paste(tmp, "tbl_ecosyst_en.tex", sep = "/"))

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/ecosysteme", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

### Distribution of PAs across countries and regions

#### Statistics at country level

```{r message=FALSE, warning=FALSE, eval = FALSE}

data_distrib_ctry = data_stat_nodupl %>%
  group_by(pays, iso3) %>%
  summarize(n = n(),
            freq = round(n/nrow(data_stat_nodupl), 1)*100) %>%
  ungroup() 


data_distrib_ctry_top = data_distrib_ctry %>%
  subset(freq >= 5)

#Histogram in share (in French) for top countries
hist_distrib_ctry_top_shr_fr = ggplot(data_distrib_ctry_top, 
                     aes(x = reorder(pays, -freq), y = freq, fill = pays)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ geom_text(aes(label = round(n, 1), y = freq), 
        vjust = -0.1, color="black",
        size=3.5) %>%
+ labs(title = "Les pays abritant le plus d'aires protégées",
       subtitle = paste("Echantillon :", sum(data_distrib_ctry$n), "aires protégées. Nombre d'aires indiqué à la base du graphique"),
         x = "Pays",
         y = "Proportion d'aires protégées(%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 0,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_distrib_ctry_top_shr_fr
# 


#Histogram in number (in French)
hist_distrib_ctry_n_fr = ggplot(data_distrib_ctry, 
                     aes(x = reorder(pays, -n), y = n, fill = pays)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ geom_text(aes(label = round(n, 1), y = n), 
        vjust = -0.1, color="black",
        size=3.5) %>%
+ labs(title = "Proportion d'aires protégées par pays",
       subtitle = paste("Echantillon :", sum(data_distrib_ctry$n), "aires protégées. Nombre d'aires indiqué sur chaque barre"),
         x = "Pays",
         y = "Proportion d'aires protégées(%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_distrib_ctry_n_fr
# 

```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "hist_distrib_ctry_top_shr_fr.png", sep = "/"),
       plot = hist_distrib_ctry_top_shr_fr,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "hist_distrib_ctry_n_fr.png", sep = "/"),
       plot = hist_distrib_ctry_n_fr,
       device = "png",
       height = 6, width = 9)

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/distribution", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

#### Statistics at region level

```{r, eval = FALSE}
data_distrib_reg = data_stat_nodupl %>%
  group_by(direction_regionale) %>%
  summarize(n = n(),
            freq = round(n/nrow(data_stat_nodupl), 3)*100) %>%
  ungroup() %>%
  mutate(region = gsub("Dr ", "", direction_regionale),
         .after = "direction_regionale")


data_distrib_reg_top = data_distrib_reg %>%
  subset(freq >= 5)

#Histogram in share (in French) for top countries
hist_distrib_reg_top_shr_fr = ggplot(data_distrib_reg_top, 
                     aes(x = reorder(region, -freq), y = freq, fill = region)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ geom_text(aes(label = round(n, 1), y = freq), 
        vjust = -0.1, color="black",
        size=3.5) %>%
+ labs(title = "Les directions régionales finançant le plus d'aires protégées",
       subtitle = paste("Echantillon :", sum(data_distrib_reg$n), "aires protégées. Nombre d'aires indiqué sur chaque barre."),
         x = "Direction régionale",
         y = "Proportion d'aires protégées(%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 0,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_distrib_reg_top_shr_fr
# 


#Histogram in number (in French)
hist_distrib_reg_n_fr = ggplot(data_distrib_reg, 
                     aes(x = reorder(direction_regionale, -n), y = n, fill = direction_regionale)) %>%
+ geom_bar(width = 0.50, fill= "#3182BD", stat="identity") %>%
+ geom_text(aes(label = round(n, 1), y = n), 
        vjust = -0.1, color="black",
        size=3.5) %>%
+ labs(title = "Proportion d'aires protégées par région",
       subtitle = paste("Echantillon :", sum(data_distrib_ctry$n), "aires protégées. Nombre d'aires indiqué sur chaque barre."),
         x = "Direction régionale",
         y = "Proportion d'aires protégées(%)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
hist_distrib_reg_n_fr

```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "hist_distrib_reg_top_shr_fr.png", sep = "/"),
       plot = hist_distrib_reg_top_shr_fr,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "hist_distrib_reg_n_fr.png", sep = "/"),
       plot = hist_distrib_reg_n_fr,
       device = "png",
       height = 6, width = 9)

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/distribution", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

### Surface of PAs

#### Distribution of surfaces

```{r, eval = FALSE}

tbl_distrib_area_no0 = summary(
  filter(data_stat_nodupl, superficie != 0)$superficie) %>%
  format(scientific = FALSE, big.mark = " ") %>%
  as.array() %>%
  t() %>%
  as.data.frame() %>%
  select(-c("1st Qu.","3rd Qu."))


```

#### Average surface in countries and regions

```{r, eval = FALSE}
#Distribution of PA WITH SURFACE >0 across countries and regions
##Country
data_distrib_no0_ctry = data_stat_nodupl %>%
  filter(superficie != 0) %>%
  group_by(iso3, pays) %>%
  summarize(n = n(),
            freq = round(n/nrow(data_stat_nodupl), 1)*100) %>%
  ungroup()

##Region
data_distrib_no0_dr = data_stat_nodupl %>%
  filter(superficie != 0) %>%
  group_by(direction_regionale) %>%
  summarize(n = n(),
            freq = round(n/nrow(data_stat_nodupl), 1)*100) %>%
  ungroup() %>%
  mutate(region = gsub("Dr ", "", direction_regionale),
         .after = "direction_regionale")

#By country..
tbl_area_avg_ctry = data_distrib_no0_ctry %>%
  select(-freq) %>%
  left_join(pa_area_ctry, by = "iso3") %>%
  select(-c(iso3, sprfc_tot_km2, tot_area_int)) %>%
  mutate(sprfc_avg_noint_km2 = format(sprfc_tot_noint_km2/n, big.mark = " ", scientific = FALSE, digits = 1),
         sprfc_tot_noint_km2 = format(sprfc_tot_noint_km2, big.mark  = " ", scientific = FALSE, digits = 1),
         )
names(tbl_area_avg_ctry) = c("Pays", "Nombre d'AP", "Superficie totale (km2)", "Superficie moyenne (km2)")

#By region
tbl_area_avg_dr = data_distrib_no0_dr %>%
  select(-freq) %>%
  left_join(pa_area_dr, by = "direction_regionale") %>%
  select(-c(sprfc_tot_km2, tot_area_int, direction_regionale)) %>%
  mutate(sprfc_avg_noint_km2 = format(sprfc_tot_noint_km2/n, big.mark = " ", scientific = FALSE, digits = 1),
         sprfc_tot_noint_km2 = format(sprfc_tot_noint_km2, big.mark  = " ", scientific = FALSE, digits = 1),
         )
names(tbl_area_avg_dr) = c("Direction régionale", "Nombre d'AP", "Superficie totale (km2)", "Superficie moyenne (km2)")


```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

print(xtable(tbl_distrib_area_no0, type = "latex"), 
      file = paste(tmp, "tbl_distrib_area_no0.tex", sep = "/"))
print(xtable(tbl_area_avg_ctry, type = "latex"), 
      file = paste(tmp, "tbl_area_avg_ctry.tex", sep = "/"))
print(xtable(tbl_area_avg_dr, type = "latex"), 
      file = paste(tmp, "tbl_area_avg_dr.tex", sep = "/"))

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/surface", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

### Temporal evolution

In this section is plotted the evolution in the number and surafe of PAs over time (cumulated number/surface and number/surface of PAs funded by year).

#### Number of PAs

```{r, eval = FALSE}

data_time_range = data.frame(annee = 
                              c(min(data_stat_nodupl$annee_octroi):max(data_stat_nodupl$annee_octroi))
)


data_time_n = data_stat_nodupl %>%
  group_by(annee_octroi) %>%
  summarize(n = n()) %>%
  full_join(data_time_range, by = c("annee_octroi" = "annee")) %>%
  mutate(n = case_when(is.na(n)~0, TRUE~n)) %>%
  arrange(annee_octroi) %>%
  mutate(n_cum = cumsum(n)) 

#Number of PAs funded by year 
fig_n_pa = ggplot(data_time_n,
                  aes(x = factor(annee_octroi), y = n)) %>%
  + geom_bar(stat = 'identity', fill = "#3182BD") %>% 
  + geom_text(aes(y = n, label = ifelse(n == 0, NA, n)), 
              color = "black", size=4, vjust = -0.3) %>%
  + labs(title = "Nombre d'aires protégées appuyées par année",
         subtitle = paste("Echantillon :", sum(data_time_n$n), "aires protégées"),
         x = "Année",
         y = "Nombre d'aires protégées") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_n_pa



#Cumulative number over time
fig_ncum_pa = ggplot(data_time_n,
                  aes(x = factor(annee_octroi), y = n_cum)) %>%
  # + geom_point(color = "#3182BD", size = 1.5) %>%
  # + geom_line(color = "#3182BD", size = 1) %>% 
  + geom_bar(stat = 'identity', fill = "#3182BD") %>%
  + geom_text(aes(y = n_cum, label = n_cum), 
              color = "black", size=4, vjust = -0.3) %>%
  + labs(title = "Evolution cumulée du nombre d'aires protégées appuyées par l'AFD",
         subtitle = paste("Echantillon :", sum(data_time_n$n), "aires protégées"),
         x = "Année",
         y = "Nombre d'aires protégées") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_ncum_pa


```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "fig_n_pa.png", sep = "/"),
       fig_n_pa,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "fig_ncum_pa.png", sep = "/"),
       fig_ncum_pa,
       device = "png",
       height = 6, width = 9)



#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/time_evolution", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

#### Surface of PAs

```{r, eval = FALSE}
data_time_range = data.frame(annee = 
                              c(min(data_stat_nodupl$annee_octroi):max(data_stat_nodupl$annee_octroi))
)


data_time_area = data_stat_nodupl %>%
  group_by(annee_octroi) %>%
  summarize(tot_area_km2 = sum(superficie)) %>%
  left_join(pa_int_yr, by = c("annee_octroi" = "annee_int")) %>%
  full_join(data_time_range, by = c("annee_octroi" = "annee")) %>%
  mutate(tot_area_km2 = case_when(is.na(tot_area_km2)~0, TRUE~tot_area_km2),
         tot_int_km2 = case_when(is.na(tot_int_km2)~0, TRUE~tot_int_km2),
         tot_area_noint_km2 = tot_area_km2 - tot_int_km2) %>%
  arrange(annee_octroi)

#Evolution of area over time
fig_area_pa = ggplot(data_time_area,
                  aes(x = factor(annee_octroi), y = tot_area_noint_km2)) %>%
  + geom_bar(stat = 'identity', fill = "#3182BD") %>%
  + geom_text(aes(y = tot_area_noint_km2, 
                  label = ifelse(tot_area_noint_km2 != 0,
                                 format(tot_area_noint_km2, 
                                        digits = 2, 
                                        scientific = TRUE),
                                 NA)), 
              color = "black", size=3, vjust = -0.3) %>%
  + labs(title = "Evolution de la superficie des aires protégées",
         subtitle = paste("Echantillon :", sum(data_time_n$n), "aires protégées couvrant", format(sum(data_time_area$tot_area_noint_km2), digits = 1, scientific = FALSE, big.mark = " "), "km2"),
         x = "Année",
         y = "Superficie (km2)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_area_pa



#Cumulative area over time
fig_area_cum_pa = ggplot(data_time_area,
                  aes(x = factor(annee_octroi),
                      y = cumsum(tot_area_noint_km2))) %>%
  # + geom_point(color = "#3182BD", size = 1.5) %>%
  # + geom_line(color = "#3182BD", size = 1) %>% 
  + geom_bar(stat = 'identity', fill = "#3182BD") %>%
  + geom_text(aes(y = cumsum(tot_area_noint_km2), 
                  label = format(cumsum(tot_area_noint_km2), 
                                 digits = 2,
                                 scientific = TRUE)), 
              color = "black", size=3, vjust = -0.3) %>%
  + labs(title = "Evolution cumulée de la superficie des aires protégées",
          subtitle = paste("Echantillon :", sum(data_time_n$n), "aires protégées couvrant", format(sum(data_time_area$tot_area_noint_km2), digits = 1, scientific = FALSE, big.mark = " "), "km2"),
         x = "Année",
         y = "Superficie (km2)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_area_cum_pa



```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "fig_area_pa.png", sep = "/"),
       fig_area_pa,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "fig_area_cum_pa.png", sep = "/"),
       fig_area_cum_pa,
       device = "png",
       height = 6, width = 9)

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/time_evolution", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

### Governance

Here is plotted the distribution of PAs across governance type.

```{r, eval = FALSE}

#Table of the governance type distribution
##English version
data_gov_en = data_stat_nodupl %>%
  mutate(gov_type = case_when(gov_type == "" ~ "Not referenced",
                              TRUE ~ gov_type)) %>%
  group_by(gov_type) %>%
  summarize(n = n()) %>%
  mutate(n_tot = sum(n),
         freq = round(n/n_tot*100,1)) %>%
  select(-n_tot) %>%
  arrange(-freq)

tbl_gov_en = data_gov_en
names(tbl_gov_en) = c("Governance","Number of PAs","Share of PAs (%)")


##French Version
data_gov_fr = data_stat_nodupl %>%
  mutate(gov_type = case_when(gov_type == "" ~ "Non référencée",
                              gov_type == "Collaborative governance" ~ "Gouvernance collaborative",
                              gov_type == "Federal or national ministry or agency" ~ "Ministère ou agence, fédérale ou nationale",
                              gov_type == "Federal or national ministry or agency" ~ "Ministère ou agence, fédérale ou nationale",
                              gov_type == "Government-delegated management" ~ "Gestion déléguée par le gouvernement",
                              gov_type == "Indigenous peoples" ~ "Peuples indigènes",
                              gov_type == "Joint governance" ~ "Gouvernance conjointe",
                              gov_type == "Local communities" ~ "Communautés locales",
                              gov_type == "Non-profit organisations" ~ "Organisations non-lucratives",
                              gov_type == "Not Reported" ~ "Non rapportée",
                              gov_type == "Sub-national ministry or agency" ~ "Ministère ou agence sous-nationale",
                              TRUE ~ gov_type)) %>%
  group_by(gov_type) %>%
  summarize(n = n()) %>%
  mutate(n_tot = sum(n),
         freq = round(n/n_tot*100,1)) %>%
  select(-n_tot) %>%
  arrange(-freq)

tbl_gov_fr = data_gov_fr
names(tbl_gov_fr) = c("Gouvernance","Nombre d'AP","Proportion (%)")



#PAs with nureported or unreferenced governance types are removed
##Tables
###English
data_gov_knwn_en = data_stat_nodupl %>%
  mutate(gov_type = case_when(gov_type == "" ~ "Not referenced",
                              TRUE ~ gov_type)) %>%
  filter(gov_type != "Not Reported" & gov_type != "Not referenced") %>%
  group_by(gov_type) %>%
  summarize(n = n()) %>%
  mutate(n_tot = sum(n),
         freq = round(n/n_tot*100,1)) %>%
  select(-n_tot) %>%
  arrange(-freq)

tbl_gov_knwn_en = data_gov_knwn_en
names(tbl_gov_knwn_en) = c("Governance","Number of PAs","Share of PAs (%)")

###French
data_gov_knwn_fr = data_stat_nodupl %>%
  mutate(gov_type = case_when(gov_type == "" ~ "Non référencée",
                              gov_type == "Collaborative governance" ~ "Gouvernance collaborative",
                              gov_type == "Federal or national ministry or agency" ~ "Ministère ou agence, fédérale ou nationale",
                              gov_type == "Federal or national ministry or agency" ~ "Ministère ou agence, fédérale ou nationale",
                              gov_type == "Government-delegated management" ~ "Gestion déléguée par le gouvernement",
                              gov_type == "Indigenous peoples" ~ "Peuples indigènes",
                              gov_type == "Joint governance" ~ "Gouvernance conjointe",
                              gov_type == "Local communities" ~ "Communautés locales",
                              gov_type == "Non-profit organisations" ~ "Organisations non-lucratives",
                              gov_type == "Not Reported" ~ "Non rapportée",
                              gov_type == "Sub-national ministry or agency" ~ "Ministère ou agence sous-nationale",
                              TRUE ~ gov_type)) %>%
  filter(gov_type != "Non référencée" & gov_type != "Non rapportée") %>%
  group_by(gov_type) %>%
  summarize(n = n()) %>%
  mutate(n_tot = sum(n),
         freq = round(n/n_tot*100,1)) %>%
  select(-n_tot) %>%
  arrange(-freq)

tbl_gov_knwn_fr = data_gov_knwn_fr
names(tbl_gov_knwn_fr) = c("Gouvernance","Nombre d'AP","Proportion (%)")
 

##Pie charts
###English
pie_gov_knwn_en = 
  ggplot(data_gov_knwn_en, 
       aes(x="", y= freq, fill= gov_type)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + geom_label(aes(x=1.3, 
                   label = paste0(format(freq, digits = 2), "%")), 
               color = "black", 
               position = position_stack(vjust = 0.55), 
               size=2.5, show.legend = FALSE) %>%
  + coord_polar("y", start=0) %>%
  + labs(title = "Governance type of PAs, except not referenced/reported PAs",
         subtitle = paste("Sample :", sum(data_gov_knwn_en$n), "PAs")) %>%
  + scale_fill_brewer(name = "Governance", palette="Paired") %>%
  + theme_void()



###French
pie_gov_knwn_fr =
  ggplot(data_gov_knwn_fr, 
       aes(x="", y= freq, fill= gov_type)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + geom_label(aes(x=1.3, 
                   label = paste0(format(freq, digits = 2), "%")), 
               color = "black", 
               position = position_stack(vjust = 0.55), 
               size=2.5, show.legend = FALSE) %>%
  + coord_polar("y", start=0) %>%
  + labs(title = "Gouvernance, hors aires protégées avec une gouvernance \nnon-rapportée/référencée",
         subtitle = paste("Echantillon :", sum(data_gov_knwn_fr$n), "aires protégées")) %>%
  + scale_fill_brewer(name = "Gouvernance", palette="Paired") %>%
  + theme_void()
pie_gov_knwn_fr

```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

print(xtable(tbl_gov_en, type = "latex"),
      file = paste(tmp, "tbl_gov_en.tex", sep  ="/"))
print(xtable(tbl_gov_fr, type = "latex"),
      file = paste(tmp, "tbl_gov_fr.tex", sep  ="/"))
print(xtable(tbl_gov_knwn_en, type = "latex"),
      file = paste(tmp, "tbl_gov_knwn_en.tex", sep  ="/"))
print(xtable(tbl_gov_knwn_fr, type = "latex"),
      file = paste(tmp, "tbl_gov_knwn_fr.tex", sep  ="/"))

ggsave(paste(tmp, " pie_gov_knwn_en.png", sep = "/"),
       plot =  pie_gov_knwn_en,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "pie_gov_knwn_fr.png", sep = "/"),
       plot = pie_gov_knwn_fr,
       device = "png",
       height = 6, width = 9)

#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
count = 0
for(f in files) 
{
  count = count+1
  cat("Uploading file", paste0(count, "/", length(files), " '", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/DesStat/gouvernance", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```
