---
title: "Confidential descriptive statistics"
author: "Antoine Vuillot"
date: "05/07/2023"
output: 
  html_document: 
    fig_caption: yes
editor_options: 
  chunk_output_type: inline
---

In this document are performed and plotted descriptive statistics of confidential data.

# Importing packages

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE}

library(tidyverse)
library(stargazer)
library(dplyr)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(data.table)
#library(readxl)
#library(splitstackshape) 
library(janitor)
library(xtable)
library(questionr)
```

# Importing datasets

```{r}
#Both datasets are imported also in UTF8 encoding, for some variables
##A first dataset with some PA on more than one row (one line per funding for instance)
data_stat_fund = 
  fread("data_tidy/BDD_DesStat_fund.csv", encoding = "UTF-8")
  # aws.s3::s3read_using(
  # FUN = data.table::fread,
  # encoding = "UTF-8",
  # # Mettre les options de FUN ici
  # object = "data_tidy/BDD_DesStat_nopub.csv",
  # bucket = "projet-afd-eva-ap",
  # opts = list("region" = ""))

pa_area_ctry = fread("data_tidy/area/pa_area_ctry.csv")
pa_area_dr = fread("data_tidy/area/pa_area_dr.csv")
pa_int_yr = fread("data_tidy/area/pa_int_yr.csv") 
load("data_tidy/area/pa_area_wld.RDdata")
```

# Descriptive statistics

## Funding

This section provides several statistics on the funding of PAs : average funding by project, by contest, average funding by region or country, average funding by area, evolution over time, funding type.

### Average funding

Create a dataset with one row per project (funding is given by project, so duplicates are avoided)

```{r}

data_stat_projet_nodupl = data_stat_fund %>%
  dplyr::distinct(id_projet, .keep_all = TRUE)

```

Distribution of project funding

```{r}

#Table
tbl_fund_proj = summary(data_stat_projet_nodupl$montant_total_projet) %>%
  format(scientific = FALSE) %>%
  t() %>%
  as.data.frame() %>%
  dplyr::select(-c("1st Qu.","3rd Qu."))

# print(xtable(tbl_fund_proj, "Latex"),
#       file = "DesStat/funding/tbl_fund_proj_stat.tex")

```

Average funds given by each concours

```{r}

data_fund_concours = data_stat_fund %>%
  group_by(id_concours) %>%
  slice(1) %>%
  ungroup()

tbl_fund_concours = 
  summary(data_fund_concours$montant_prevu_concours_euro_octroi) %>%
  format(scientific = FALSE) %>%
  t() %>%
  as.data.frame() %>%
  dplyr::select(-c("1st Qu.","3rd Qu."))

# print(xtable(tbl_fund_concours, "Latex"),
#       file = "DesStat/funding/tbl_fund_concours_stat.tex")

```

**Average fund received by each project in the different concours**

```{r}

# tbl_fund_project_concours = data_stat_fund %>%
#   group_by(id_projet) %>%
#   summarize(Mean = mean(montant_prevu_concours_euro_octroi))

```

**Funding by country/region**

```{r}
#Careful, a project can cover more than one countries. For instance ;
#CZZ1260; CZZ1282; CZZ1382; CZZ1419; CZZ1667; CZZ1879, CZZ1909; 	
#CZZ1914; CZZ3012; CZZ3092 ...
#From the data we have, it is not possible to decompose the funding of a project between the different countries. Thus only regional/world statistics are performed here.


#By country ...
# tbl_fund_avg_ctry = data_stat_projet_nodupl %>%
#   group_by(pays, iso3) %>%
#   summarize(avg_fund = mean(montant_total_projet, na.rm = TRUE)) %>%
#   arrange(avg_fund)

#By region
##Average fund 
###Creating dataset
data_fund_avg_dr = data_stat_projet_nodupl %>%
  group_by(direction_regionale) %>%
  summarise(n_proj = n(),
            avg_fund = mean(montant_total_projet, na.rm = TRUE)) %>%
  arrange(avg_fund)

###Figure
fig_fund_avg_dr = ggplot(data = data_fund_avg_dr,
                         aes(x = direction_regionale, y = avg_fund,
                             fill = direction_regionale)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = n_proj, y = avg_fund), 
            vjust = -0.2, color="black",
            size=3.5) %>%
  + labs(title = "Fonds moyens alloués aux projets par région",
         subtitle = paste("Echantillon :", sum(data_fund_avg_dr$n_proj), "projets. Nombre de projets indiqué sur les barres."),
          x = "", 
          y = "Montant (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_avg_dr

# ggsave(plot = fig_fund_avg_dr,
#        filename = "fig_fund_avg_dr.png",
#        path = "DesStat/funding",
#        device = "png",
#        height = 6, width = 9)

###Table

tbl_fund_avg_dr = data_fund_avg_dr
names(tbl_fund_avg_dr) = c("Direction régionale",
                           "Nombre de projets",
                           "Montant moyen (€)")

# print(xtable(tbl_fund_avg_dr, type = "latex"),
#       file = "DesStat/funding/tbl_fund_avg_dr.tex")

##Total fund
###Creating dataset
data_fund_tot_dr = data_stat_projet_nodupl %>%
  group_by(direction_regionale) %>%
  summarise(n_proj = n(),
            tot_fund = sum(montant_total_projet, na.rm = TRUE)) %>%
  arrange(tot_fund)

###Figure
fig_fund_tot_dr = ggplot(data = data_fund_tot_dr,
                         aes(x = direction_regionale, y = tot_fund,
                             fill = direction_regionale)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = n_proj, y = tot_fund), 
            vjust = -0.2, color="black",
            size=3.5) %>%
  + labs(title = "Total des fonds alloués aux projets par région",
         subtitle = paste("Echantillon :", sum(data_fund_tot_dr$n_proj), "projets. Nombre de projets indiqué sur les barres."),
          x = "", 
          y = "Montant (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_tot_dr

# ggsave(plot = fig_fund_tot_dr,
#        filename = "fig_fund_tot_dr.png",
#        path = "DesStat/funding",
#        device = "png",
#        height = 6, width = 9)

###Table

###Table

tbl_fund_tot_dr = data_fund_tot_dr
names(tbl_fund_tot_dr) = c("Direction régionale",
                           "Nombre de projets",
                           "Montant total (€)")

# print(xtable(tbl_fund_tot_dr, type = "latex"),
#       file = "DesStat/funding/tbl_fund_tot_dr.tex")

```

**Average funding per unit or area (marine and terrestrial), at regional and world level**

Some projects cover more than one country (e.g CZZ3012), but the total fund is given at project level. Thus it is not possible to compute funding per unit of area at country level for all countries.

It is possible however at DR level. Note that the total surface at world level is different from the total surface from the DR, taking the overlap into account. Indeed, overlap between polygons from different DR is subtracted at world level but not at DR level.

```{r}
#By country ...
# data_fund_sum_ctry = data_stat_projet_nodupl %>%
#   group_by(pays, iso3) %>%
#   summarize(tot_fund = sum(montant_total_projet, na.rm = TRUE)) %>%
#   ungroup() %>%
#   arrange(tot_fund) 
# 
# data_fund_per_area_ctry = data_fund_sum_ctry %>%
#   left_join(select(pa_area_ctry, c(iso3, sprfc_tot_noint_km2)), by = "iso3") %>%
#   mutate(fund_per_area = tot_fund/sprfc_tot_noint_km2)
# names(data_fund_per_area_ctry) = c("Pays", "ISO3", "Montant total (€)", "Superficie totale (km2)", "Financement moyen par km2 (€/km2)")
#print(xtable(data_fund_per_area_ctry, type = "latex"), file = "DesStat/funding/tbl_fund_per_area_ctry.tex")


#By region 
##Creating the datasets
data_fund_tot_dr = data_stat_projet_nodupl %>%
  group_by(direction_regionale) %>%
  summarise(n_proj = n(),
            tot_fund = sum(montant_total_projet, na.rm = TRUE)) %>%
  arrange(tot_fund)

data_fund_per_area_dr = data_fund_tot_dr %>%
  left_join(select(pa_area_dr, c(direction_regionale, sprfc_tot_noint_km2)), by = "direction_regionale") %>%
  mutate(fund_per_area = tot_fund/sprfc_tot_noint_km2)

##Figure
fig_fund_per_area_dr = ggplot(data = data_fund_per_area_dr,
                         aes(x = direction_regionale, y = fund_per_area,
                             fill = direction_regionale)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = format(fund_per_area, scientific = TRUE, digits = 2),
                  y = fund_per_area), 
            vjust = -0.2, color="black",
            size=2.5) %>%
  + labs(title = "Fonds moyens alloués par km2",
          x = "", 
          y = "Montant par surface (€/km2)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_per_area_dr

# ggsave(plot = fig_fund_per_area_dr,
#        filename = "fig_fund_per_area_dr.png",
#        path = "DesStat/funding",
#        device = "png",
#        height = 6, width = 9)

##Table
tbl_fund_per_area_dr = data.frame(data_fund_per_area_dr) %>%
  select(-n_proj) %>%
  format(digits = 4)
names(tbl_fund_per_area_dr) = c("Direction régionale", "Montant total (€)", "Superficie totale (km2)", "Financement moyen par km2 (€/km2)")

# print(xtable(tbl_fund_per_area_dr, type = "latex"),
#       file = "DesStat/funding/tbl_fund_per_area_dr.tex")


#At world level
##Table
data_fund_per_area_wld = sum(data_stat_projet_nodupl$montant_total_projet)/pa_area_wld
tbl_fund_per_area_wld = data.frame(data_fund_per_area_wld) %>% format(digits = 4)
names(tbl_fund_per_area_wld) = c("Financement moyen par km2 (€/km2)")

# print(xtable(tbl_fund_per_area_wld, type = "latex"),
#       file = "DesStat/funding/tbl_fund_per_area_wld.tex")

```

### Evolution of funding over time

```{r}
data_fund_year = data_stat_projet_nodupl %>%
  group_by(annee_octroi) %>%
  summarize(tot_fund = sum(montant_total_projet))

#Total funding for each year
fig_fund_year = ggplot(data = data_fund_year,
                       aes(x = annee_octroi, y = tot_fund)) %>%
  + geom_bar(stat = 'identity', fill = "#3182BD") %>% 
  + geom_text(aes(y = tot_fund, label = format(tot_fund, scientific = TRUE, digits = 2)),
              color = "black", size=2.5, vjust = -0.3) %>%
  + labs(title = "Evolution du financement des aires protégées",
         x = "Année",
         y = "Montants octroyés (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
#fig_fund_year

# ggsave(plot = fig_fund_year,
#        filename = "fig_fund_year.png",
#        path = "DesStat/funding",
#        device = "png",
#        height = 6, width = 9)

#Cumulative funding over time
fig_fund_year_cum = ggplot(data = data_fund_year,
                       aes(x = annee_octroi, y = cumsum(tot_fund))) %>%
  + geom_bar(stat = 'identity', fill = "#3182BD") %>% 
  + geom_text(aes(y = cumsum(tot_fund), label = format(cumsum(tot_fund), scientific = TRUE, digits = 2)),
              color = "black", size=2.5, vjust = -0.3) %>%
  + labs(title = "Evolution cumulée du financement des aires protégées",
         x = "Année",
         y = "Montants octroyés (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_year_cum

# ggsave(plot = fig_fund_year_cum,
#        filename = "fig_fund_year_cum.png",
#        path = "DesStat/funding",
#        device = "png",
#        height = 6, width = 9)

```

### Type of funding

Distribution of funding types

```{r}

data_type_prod = data_stat_projet_nodupl %>%
  group_by(libelle_produit) %>%
  #number of PAs per funding type
  summarize(n_type = n()) %>%
  ungroup() %>%
  #Frequency of funding types
  mutate(n_pa = sum(n_type),
         freq = round(n_type/n_pa*100, 1),
         libelle_produit = case_when(libelle_produit == "PRETS SOUVERAINS FMI COMPATIBLE" ~ "Prêts souverains FMI-compatible", TRUE ~ libelle_produit)) %>%
  arrange(desc(libelle_produit)) %>%
  select(-n_pa) %>%
  arrange(-freq)

tbl_type_prod = data_type_prod
names(tbl_type_prod) <- c("Type de financement","Projets", "Proportion (%)")

# print(xtable(tbl_type_prod, type = "latex"),
#       file = "DesStat/funding/tbl_fund_type.tex")

#Pie chart INcluding non-referenced PAs
pie_type_prod = ggplot(data_type_prod, 
                      aes(x="", y= freq, fill = libelle_produit)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, 
                         label = paste0(round(freq, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Type de financement") %>%
  + scale_fill_brewer(name = "Catégories", palette = "Dark2") %>%
  + theme_void()
pie_type_prod

# ggsave(plot = pie_type_prod,
#        filename = "pie_type_prod.png",
#        path = "DesStat/funding",
#        device = "png",
#        height = 6, width = 9)
```

Average fund by funding type

```{r}

tbl_fund_avg_type = data_stat_projet_nodupl %>%
  group_by(libelle_produit) %>%
  summarize(n_type = n(),
            tot_fund = sum(montant_total_projet)
            ) %>%
  mutate(n_pa = sum(n_type),
         freq_pa = round(n_type/n_pa*100, 1),
         freq_fund = round(tot_fund/sum(tot_fund)*100, 1),
         libelle_produit = case_when(libelle_produit == "PRETS SOUVERAINS FMI COMPATIBLE" ~ "Prêts souverains FMI-compatible", TRUE ~ libelle_produit),
         tot_fund = format(tot_fund, big.mark = " ")) %>%
  select(c(libelle_produit, n_type, freq_pa, tot_fund, freq_fund)) %>%
  arrange(-freq_pa) 
names(tbl_fund_avg_type) = c("Type de financement","Projets", "Proportion d'AP (%)", "Montants (€)", "Proportion des montants (%)")

# print(xtable(tbl_fund_avg_type, type = "latex"),
#       file = "DesStat/funding/tbl_fund_avg_type.tex")

```

### Co-funders

```{r}
#Create a table with number of projects funded by AFD, FFEM and KfW. Total fundings and average funds are also reported
tbl_fund_cofunder = 
  data.frame(cof = c("FFEM", "KfW"),
             n = c(nrow(subset(data_stat_projet_nodupl, ffem_bin == TRUE)),
                   nrow(subset(data_stat_projet_nodupl, kfw_bin == TRUE))),
             fund_tot = c(sum(subset(data_stat_projet_nodupl, ffem_bin == TRUE)$montant_total_projet, na.rm = TRUE),
               sum(subset(data_stat_projet_nodupl, kfw_bin == TRUE)$montant_total_projet, na.rm = TRUE))
                               
                               ) %>%
  mutate(n_tot = nrow(data_stat_projet_nodupl),
         freq = round(n/n_tot*100, 1),
         fund_avg = fund_tot/n,
         fund_tot = format(fund_tot, big.mark = " "),
         fund_avg = format(fund_avg, big.mark = " ")) %>%
  select(c(cof, n, n_tot, freq, fund_tot, fund_avg))
names(tbl_fund_cofunder) = c("Cofinancier", "Nombre projets", "Nombre total projets", "Prop. projets (%)","Montant total projets (€)","Montant moyen projets (€)")

# print(xtable(tbl_fund_cofunder, type = "latex"), file = "DesStat/funding/tbl_fund_cofunder.tex")


```
