# Generating maps

## Importing relevant packages

# `{r setup, include = FALSE, eval = FALSE} # knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file()) #`

```{r message=TRUE, warning=TRUE, eval = FALSE}
install.packages(c("janitor", "wdpar", "countrycode"))
library(tidyverse)
library(dplyr)
library(data.table)
library(readxl)
library(janitor)
library(stringi)
library(sf)
library(terra)
library(mapview)
library(wdpar)
library(aws.s3)
library(countrycode)

#Install webdriver to download WDPA data
#webdriver::install_phantomjs()

```

## Importing datasets

```{r, eval = FALSE}

#Import dataset of PAs (1 row = 1 PA)
data_pa_fund_nodupl = 
  #fread("data_raw/BDD_PA_AFD_fund_nodupl.csv")
  s3read_using(readr::read_delim,
               delim = ";",
               show_col_types = FALSE,
               object = "data_tidy/BDD_PA_AFD_fund_nodupl.csv",
              bucket = "projet-afd-eva-ap",
              opts = list("region" = ""))

data_pa_fund_wdpa = data_pa_fund_nodupl %>%
  filter(is.na(wdpaid) == FALSE)
#Define a list of iso to download WDPA data
list_iso = data_pa_fund_wdpa %>%
  filter(!(iso3 %in% c("COG;CMR;CAF", "ZZ") | is.na(iso3))) %>%
  select(iso3) %>%
  unique() 
list_iso = list_iso$iso3

#Import WDPA data
##Either download and store it ...
# data_wdpa = wdpa_fetch(x = list_iso, wait = TRUE, download_dir = "data_raw",
#                        page_wait = 2, verbose = TRUE)
# st_write(wdpa,
#          dsn = "data_raw/wdpa/wdpa_shp_global_raw.gpkg",
#          delete_dsn = TRUE)
# s3write_using(x = data_wdpa,
#               FUN = sf::st_write,
#               object = "data_raw/wdpa/17_08_2023/wdpa_shp_global_raw.gpkg",
#               bucket = "projet-afd-eva-ap",
#               opts = list("region" = ""))

##... or import it from SSP Cloud
data_wdpa =
  #st_read("data_raw/wdpa/wdpa_shp_global_raw.gpkg") %>%
  s3read_using(sf::st_read,
              object = "data_raw/wdpa/wdpa_shp_global_raw.gpkg",
              bucket = "projet-afd-eva-ap",
              opts = list("region" = "")) %>%
  clean_names() %>%
  select(c(wdpaid, wdpa_pid, geom)) %>%
  mutate(geom_type = st_geometry_type(geom))


#Polygons from WDPA are added to the PAs funded
data_pa_fund_shp = data_pa_fund_wdpa %>%
  left_join(data_wdpa, by = c("wdpaid", "wdpa_pid"))

# s3write_using(x = data_pa_fund_shp,
#               FUN = sf::st_write,
#               object = "data_tidy/BDD_PA_AFD_fund_shp.gpkg",
#               bucket = "projet-afd-eva-ap",
#               opts = list("region" = ""))

```

TO DO

-   Import a dataframe of results (PA ID and treatment effect amplitude, significance)

-   Merge it with WDPA to get location and shape file

-   Download country borders (all or list of countries or one country ??)

-   use tmap to do the following

    -   One representation for FAPBM/non-FAPBM

    -   Continuous scale for the TE amplitude 5 or 10 years

    -   The name of the PA (if not too long) ?

    -   
