---
title: "Confidential descriptive statistics"
author: "Antoine Vuillot"
date: "05/07/2023"
output: 
  html_document: 
    fig_caption: yes
editor_options: 
  chunk_output_type: inline
---

In this document are performed and plotted descriptive statistics of confidential data.

# Importing packages

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

```{r message=FALSE, warning=FALSE, eval = FALSE}
install.packages(c("stargazer", "janitor", "questionr", "countrycode"))
library(tidyverse)
library(stargazer)
library(dplyr)
library(sf)
library(ggplot2)
library(ggrepel)
library(RColorBrewer)
library(countrycode)
library(data.table)
#library(readxl)
#library(splitstackshape) 
library(janitor)
library(xtable)
library(questionr)
library(aws.s3)
```

# Importing datasets

```{r}
#Both datasets are imported also in UTF8 encoding, for some variables
##A first dataset with some PA on more than one row (one line per funding for instance)
## Description of funding variables (Léa Poulin, mail 16/08/2023)
### mt_global_projet_prevu_devise : total funding planned for the project (€), including local participation and cofunders
### mt_fin_global_af_d_prevu_devise : total AFD funding for the project (€)
### montant_prevu_concours_euro_octroi : planned funding in the concours considered
### mt_part_cofinancier_prevu_euro : funding planed by the cofunder considered
data_stat_fund = 
  #fread("data_tidy/BDD_PA_AFD_fund.csv")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/BDD_PA_AFD_fund.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

##Datasets on aggregated size per country/region/year and at world level, taking into account the overlap.
pa_area_ctry = 
  #fread("data_tidy/area/pa_area_ctry.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_area_ctry.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_area_region =
  #fread("data_tidy/area/pa_area_region.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_area_region.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_area_wld = 
  #fread("data_tidy/area/pa_area_wld.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_area_wld.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

pa_int_yr = 
  #fread("data_tidy/area/pa_area_region.csv", encoding = "UTF-8")
  aws.s3::s3read_using(
  FUN = data.table::fread,
  encoding = "UTF-8",
  # Mettre les options de FUN ici
  object = "data_tidy/area/pa_int_yr.csv",
  bucket = "projet-afd-eva-ap",
  opts = list("region" = ""))

```

# Descriptive statistics

This section provides several statistics on the funding of PAs : average funding by project, by contest, average funding by region or country, average funding by area, evolution over time, funding type.

## Statistics on project funding and concours

Create a dataset with one row per project (funding is given by project, so duplicates are avoided)

```{r}

data_stat_projet_nodupl = data_stat_fund %>%
  dplyr::distinct(id_projet, .keep_all = TRUE)

```

Distribution of project funding

```{r}

#Table
# tbl_fund_proj = summary(data_stat_projet_nodupl$mt_fin_global_af_d_prevu_devise) %>%
#   format(scientific = FALSE) %>%
#   t() %>%
#   as.data.frame() %>%
#   dplyr::select(-c("1st Qu.","3rd Qu."))

# print(xtable(tbl_fund_proj, "Latex"),
#       file = "descriptive_stats/funding/tbl_fund_proj_stat.tex")

```

Average funds given by each concours

```{r}

# data_fund_concours = data_stat_fund %>%
#   group_by(id_concours) %>%
#   slice(1) %>%
#   ungroup()
# 
# tbl_fund_concours = 
#   summary(data_fund_concours$mt_fin_global_af_d_prevu_devise) %>%
#   format(scientific = FALSE) %>%
#   t() %>%
#   as.data.frame() %>%
#   dplyr::select(-c("1st Qu.","3rd Qu."))

# print(xtable(tbl_fund_concours, "Latex"),
#       file = "descriptive_stats/funding/tbl_fund_concours_stat.tex")

```

**Average fund received by each project in the different concours**

```{r}

# tbl_fund_project_concours = data_stat_fund %>%
#   group_by(id_projet) %>%
#   summarize(Mean = mean(mt_fin_global_af_d_prevu_devise))

```

## **Distribution of funding by region**

```{r}
#Careful, a project can cover more than one countries. For instance ;
#CZZ1260; CZZ1282; CZZ1382; CZZ1419; CZZ1667; CZZ1879, CZZ1909; 	
#CZZ1914; CZZ3012; CZZ3092 ...
#From the data we have, it is not possible to decompose the funding of a project between the different countries. Thus only regional/world statistics are performed here.


#By region
##Number of fundings
###Creating the plot dataset
data_fund_n_region = data_stat_projet_nodupl %>%
  group_by(region) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(freq_n = round(n/sum(n)*100, 2),
         ypos_n = cumsum(freq_n) - 0.5*freq_n) %>%
  mutate(region = case_when(is.na(region) ~ "Unknown",
                            TRUE ~region))

###Figure
fig_fund_n_region = ggplot(data = data_fund_n_region,
                         aes(x = reorder(region, -n), y = n,
                             fill = region)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = format(n, digits = 2, scientific = TRUE), y = n), 
            vjust = -0.2, color="black",
            size=3.5) %>%
  + labs(title = "Number of AFD projects related to protected areas by region",
         subtitle = paste("Sample :", sum(data_fund_n_region$n), "projects"),
         caption = "Unknown corresponds to projects supervised by 'DR Siege de Paris' and whose destination region is unknown.",
          x = "", 
          y = "Number") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
fig_fund_n_region



###Pie

pie_fund_n_region = ggplot(data_fund_n_region, 
                      aes(x="", y= freq_n, fill = region)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_n, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Distribution of AFD projects related to protected areas, by region",
         subtitle = paste("Sample :", sum(data_fund_n_region$n), "projects"),
         caption = "Unknown corresponds to projects supervised by 'DR Siege de Paris' and whose destination region is unknown.") %>%
  + scale_fill_brewer(name = "Region", palette = "Dark2") %>%
  + theme_void()
pie_fund_n_region

##Average fund 
###Creating dataset
data_fund_avg_region = data_stat_projet_nodupl %>%
  group_by(region) %>%
  summarise(n_proj = n(),
            avg_fund = mean(mt_fin_global_af_d_prevu_devise, na.rm = TRUE)) %>%
  arrange(avg_fund)


###Figure
fig_fund_avg_region = ggplot(data = data_fund_avg_region,
                         aes(x = reorder(region, -avg_fund), y = avg_fund,
                             fill = region)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = format(avg_fund, digits = 2, scientific = TRUE), y = avg_fund),
            vjust = -0.2, color="black",
            size=3.5) %>%
  + labs(title = "Average AFD funding by region for project related to protected areas",
         subtitle = paste("Sample :", sum(data_fund_avg_region$n_proj), "projects"),
          x = "", 
          y = "Amount (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
fig_fund_avg_region

###Table

# tbl_fund_avg_region = data_fund_avg_region
# names(tbl_fund_avg_dr) = c("Region",
#                            "Number of projetcs",
#                            "Average amount (€)")


##Total fund
###Creating dataset
data_fund_tot_region = data_stat_projet_nodupl %>%
  group_by(region) %>%
  summarise(n_proj = n(),
            tot_fund = sum(mt_fin_global_af_d_prevu_devise, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(freq_fund = round(tot_fund/sum(tot_fund)*100, 2),
         ypos_fund = cumsum(freq_fund) - 0.5*freq_fund) %>%
  mutate(region = case_when(is.na(region) ~ "Unknown",
                            TRUE ~region))



###Figure
fig_fund_tot_region = ggplot(data = data_fund_tot_region,
                         aes(x = reorder(region, -tot_fund), y = tot_fund,
                             fill = region)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = format(tot_fund, big.mark = ","), y = tot_fund), 
            vjust = -0.2, color="black",
            size=3.5) %>%
  + labs(title = "Total AFD funding by region for project related to protected areas",
         subtitle = paste("Total AFD funding :", format(sum(data_fund_tot_region$tot_fund), big.mark = ","), "€"),
         caption = "Unknown corresponds to fund allocated by 'DR Siege de Paris' and whose destination region is unknown.",
          x = "", 
          y = "Amount (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
fig_fund_tot_region


###Pie

pie_fund_tot_region = ggplot(data_fund_tot_region, 
                      aes(x="", y= freq_fund, fill = region)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_fund, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Distribution of AFD funding related to protected areas, by region",
         subtitle = paste("Total AFD funding :", format(sum(data_fund_tot_region$tot_fund), big.mark = ","), "€"),
         caption = "Unknown corresponds to fund allocated by 'DR Siege de Paris' and whose destination region is unknown.") %>%
  + scale_fill_brewer(name = "Region", palette = "Dark2") %>%
  + theme_void()
pie_fund_tot_region

###Table

# tbl_fund_tot_region = data_fund_tot_region
# names(tbl_fund_tot_dr) = c("Region",
#                            "Number of projects",
#                            "Total amount (€)")



```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "fig_fund_n_region.png", sep = "/"),
       plot = fig_fund_n_region,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "pie_fund_n_region.png", sep = "/"),
       plot = pie_fund_n_region,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "fig_fund_avg_region.png", sep = "/"),
       plot = fig_fund_avg_region,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "fig_fund_tot_region.png", sep = "/"),
       plot = fig_fund_tot_region,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "pie_fund_tot_region.png", sep = "/"),
       plot = pie_fund_tot_region,
       device = "png",
       height = 6, width = 9)


# print(xtable(tbl_fund_avg_region, type = "latex"),
#       file = paste(tmp, "tbl_fund_avg_region.tex", sep = "/"))

# print(xtable(tbl_fund_tot_region, type = "latex"),
#       file = paste(tmp, "tbl_fund_tot_region.tex", sep = "/"))


#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/descriptive_stats/funding", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

For Asia

```{r}
#Careful, a project can cover more than one countries. For instance ;
#CZZ1260; CZZ1282; CZZ1382; CZZ1419; CZZ1667; CZZ1879, CZZ1909; 	
#CZZ1914; CZZ3012; CZZ3092 ...
#From the data we have, it is not possible to decompose the funding of a project between the different countries. Thus only regional/world statistics are performed here.


#By region
##Number of fundings
###Creating the plot dataset
data_fund_n_country = data_stat_projet_nodupl %>%
  filter(region == "Africa") %>%
  group_by(country_en) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(freq_n = round(n/sum(n)*100, 2),
         ypos_n = cumsum(freq_n) - 0.5*freq_n) %>%
  mutate(country = case_when(is.na(country_en) ~ "Unknown",
                            TRUE ~country_en))

# ###Figure
# fig_fund_n_region = ggplot(data = data_fund_n_region,
#                          aes(x = reorder(region, -n), y = n,
#                              fill = region)) %>%
#   + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
#   + geom_text(aes(label = format(n, digits = 2, scientific = TRUE), y = n), 
#             vjust = -0.2, color="black",
#             size=3.5) %>%
#   + labs(title = "Number of AFD projects related to protected areas by region",
#          subtitle = paste("Sample :", sum(data_fund_n_region$n), "projects"),
#          caption = "Unknown corresponds to projects supervised by 'DR Siege de Paris' and whose destination region is unknown.",
#           x = "", 
#           y = "Number") %>%
#   + theme(legend.position = "bottom",
#       legend.key = element_rect(fill = "white"),
#       plot.title = element_text(size = 14, face = "bold"), 
#       axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
#       panel.background = element_rect(fill = 'white', colour = 'white', 
#                                       linewidth = 0.5, linetype = 'solid'),
#       panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
#       panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
#       plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
# fig_fund_n_region



###Pie

pie_fund_n_country = ggplot(data_fund_n_country, 
                      aes(x="", y= freq_n, fill = country_en)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_n, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Distribution of AFD projects in Africa related to protected areas, by country",
         subtitle = paste("Sample :", sum(data_fund_n_country$n), "projects")) %>%
  # + scale_fill_brewer(name = "Country", palette = "Dark2") %>%
  + theme_void()
pie_fund_n_country

# ##Average fund 
# ###Creating dataset
# data_fund_avg_region = data_stat_projet_nodupl %>%
#   group_by(region) %>%
#   summarise(n_proj = n(),
#             avg_fund = mean(mt_fin_global_af_d_prevu_devise, na.rm = TRUE)) %>%
#   arrange(avg_fund)
# 
# 
# ###Figure
# fig_fund_avg_region = ggplot(data = data_fund_avg_region,
#                          aes(x = reorder(region, -avg_fund), y = avg_fund,
#                              fill = region)) %>%
#   + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
#   + geom_text(aes(label = format(avg_fund, digits = 2, scientific = TRUE), y = avg_fund),
#             vjust = -0.2, color="black",
#             size=3.5) %>%
#   + labs(title = "Average AFD funding by region for project related to protected areas",
#          subtitle = paste("Sample :", sum(data_fund_avg_region$n_proj), "projects"),
#           x = "", 
#           y = "Amount (€)") %>%
#   + theme(legend.position = "bottom",
#       legend.key = element_rect(fill = "white"),
#       plot.title = element_text(size = 14, face = "bold"), 
#       axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
#       panel.background = element_rect(fill = 'white', colour = 'white', 
#                                       linewidth = 0.5, linetype = 'solid'),
#       panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
#       panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
#       plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
# fig_fund_avg_region
# 
# ###Table
# 
# # tbl_fund_avg_region = data_fund_avg_region
# # names(tbl_fund_avg_dr) = c("Region",
# #                            "Number of projetcs",
# #                            "Average amount (€)")
# 

##Total fund
###Creating dataset
data_fund_tot_country = data_stat_projet_nodupl %>%
  filter(region == "Africa") %>%
  group_by(country_en) %>%
  summarise(n_proj = n(),
            tot_fund = sum(mt_fin_global_af_d_prevu_devise, na.rm = TRUE)) %>%
  ungroup() %>%
  mutate(freq_fund = round(tot_fund/sum(tot_fund)*100, 2),
         ypos_fund = cumsum(freq_fund) - 0.5*freq_fund) %>%
  mutate(country = case_when(is.na(country_en) ~ "Unknown",
                            TRUE ~country_en))



###Figure
# fig_fund_tot_region = ggplot(data = data_fund_tot_region,
#                          aes(x = reorder(region, -tot_fund), y = tot_fund,
#                              fill = region)) %>%
#   + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
#   + geom_text(aes(label = format(tot_fund, big.mark = ","), y = tot_fund), 
#             vjust = -0.2, color="black",
#             size=3.5) %>%
#   + labs(title = "Total AFD funding by region for project related to protected areas",
#          subtitle = paste("Total AFD funding :", format(sum(data_fund_tot_region$tot_fund), big.mark = ","), "€"),
#          caption = "Unknown corresponds to fund allocated by 'DR Siege de Paris' and whose destination region is unknown.",
#           x = "", 
#           y = "Amount (€)") %>%
#   + theme(legend.position = "bottom",
#       legend.key = element_rect(fill = "white"),
#       plot.title = element_text(size = 14, face = "bold"), 
#       axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
#       panel.background = element_rect(fill = 'white', colour = 'white', 
#                                       linewidth = 0.5, linetype = 'solid'),
#       panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
#       panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
#       plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
# fig_fund_tot_region


###Pie

pie_fund_tot_country = ggplot(data_fund_tot_country, 
                      aes(x="", y= freq_fund, fill = country_en)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_fund, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Distribution of AFD funding in Africa related to protected areas, by country",
         subtitle = paste("Total AFD funding :", format(sum(data_fund_tot_country$tot_fund), big.mark = ","), "€")) %>%
  # + scale_fill_brewer(name = "Country", palette = "Dark2") %>%
  + theme_void()
pie_fund_tot_country

###Table

# tbl_fund_tot_region = data_fund_tot_region
# names(tbl_fund_tot_dr) = c("Region",
#                            "Number of projects",
#                            "Total amount (€)")


```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "pie_fund_n_africa.png", sep = "/"),
       plot = pie_fund_n_country,
       device = "png",
       height = 6, width = 9)


ggsave(paste(tmp, "pie_fund_tot_africa.png", sep = "/"),
       plot = pie_fund_tot_country,
       device = "png",
       height = 6, width = 9)


# print(xtable(tbl_fund_avg_region, type = "latex"),
#       file = paste(tmp, "tbl_fund_avg_region.tex", sep = "/"))

# print(xtable(tbl_fund_tot_region, type = "latex"),
#       file = paste(tmp, "tbl_fund_tot_region.tex", sep = "/"))


#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/descriptive_stats/funding", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

## **Average funding per unit of area (marine and terrestrial), at regional and world level**

Some projects cover more than one country (e.g CZZ3012), but the total fund is given at project level. Thus it is not possible to compute funding per unit of area at country level for all countries.

It is possible however at region level. Note that the total surface at world level is different from the total surface from the region, taking the overlap into account. Indeed, overlap between polygons from different region is subtracted at world level but not at region level.

```{r}
#By country ...
# data_fund_sum_ctry = data_stat_projet_nodupl %>%
#   group_by(pays, iso3) %>%
#   summarize(tot_fund = sum(montant_total_projet, na.rm = TRUE)) %>%
#   ungroup() %>%
#   arrange(tot_fund) 
# 
# data_fund_per_area_ctry = data_fund_sum_ctry %>%
#   left_join(select(pa_area_ctry, c(iso3, sprfc_tot_noint_km2)), by = "iso3") %>%
#   mutate(fund_per_area = tot_fund/sprfc_tot_noint_km2)
# names(data_fund_per_area_ctry) = c("Pays", "ISO3", "Montant total (€)", "Superficie totale (km2)", "Financement moyen par km2 (€/km2)")
#print(xtable(data_fund_per_area_ctry, type = "latex"), file = "descriptive_stats/funding/tbl_fund_per_area_ctry.tex")


#By region 
##Creating the datasets
data_fund_tot_region = data_stat_projet_nodupl %>%
  group_by(region) %>%
  summarise(n_proj = n(),
            tot_fund = sum(mt_fin_global_af_d_prevu_devise, na.rm = TRUE)) %>%
  arrange(tot_fund)

data_fund_per_area_region = data_fund_tot_region %>%
  left_join(select(pa_area_region, c(region, area_tot_noint_km2)), by = "region") %>%
  mutate(fund_per_area = tot_fund/area_tot_noint_km2) %>%
  mutate(region = case_when(is.na(region) ~ "Unknown",
                            TRUE ~region))

##Figure
fig_fund_per_area_region = ggplot(data = data_fund_per_area_region,
                         aes(x = region, y = fund_per_area,
                             fill = region)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = format(fund_per_area, big.mark = ",", digits = 1),
                  y = fund_per_area), 
            vjust = -0.2, color="black",
            size=2.5) %>%
  + labs(title = "Average fund per unit of area",
          x = "", 
          y = "Funding per area (€/km²)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_per_area_region


##Table
# tbl_fund_per_area_region = data.frame(data_fund_per_area_region) %>%
#   select(-n_proj) %>%
#   format(digits = 4)
# names(tbl_fund_per_area_region) = c("Direction régionale", "Montant total (€)", "Superficie totale (km2)", "Financement moyen par km2 (€/km2)")

# print(xtable(tbl_fund_per_area_region, type = "latex"),
#       file = "descriptive_stats/funding/tbl_fund_per_area_region.tex")


#At world level
##Table
# data_fund_per_area_wld = sum(data_stat_projet_nodupl$mt_fin_global_af_d_prevu_devise)/pa_area_wld
# tbl_fund_per_area_wld = data.frame(data_fund_per_area_wld) %>% format(digits = 4)
# names(tbl_fund_per_area_wld) = c("Financement moyen par km2 (€/km2)")

# print(xtable(tbl_fund_per_area_wld, type = "latex"),
#       file = "descriptive_stats/funding/tbl_fund_per_area_wld.tex")

```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "fig_fund_per_area_region.png", sep = "/"),
       plot = fig_fund_per_area_region,
       device = "png",
       height = 6, width = 9)



#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/descriptive_stats/funding", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

## Evolution of funding over time

```{r}

data_time_range = data.frame(year = 
                              c(min(data_stat_fund$year_funding, na.rm = TRUE):max(data_stat_fund$year_funding, na.rm = TRUE))
)

data_fund_year = data_stat_projet_nodupl %>%
  group_by(year_funding) %>%
  summarize(tot_fund = sum(mt_fin_global_af_d_prevu_devise)) %>%
  full_join(data_time_range, by = c("year_funding" = "year")) %>%
  ungroup() %>%
  mutate(tot_fund = case_when(is.na(tot_fund) ~0,
                                    TRUE ~tot_fund)) %>%
  drop_na() %>%
  arrange(year_funding)

#Total funding for each year
fig_fund_year = ggplot(data = data_fund_year,
                       aes(x = year_funding, y = tot_fund)) %>%
  + geom_bar(stat = 'identity', fill = "#3182BD") %>% 
  + geom_text(aes(y = tot_fund, label = format(tot_fund, big.mark = ",", digits = 1)),
              color = "black", size=2.5, vjust = -0.3) %>%
  + labs(title = "Time evolution of AFD funding related to protected areas",
         subtitle = paste(format(sum(data_fund_year$tot_fund), big.mark = ","), "€ total funding"),
         x = "",
         y = "Funding (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_year


#Cumulative funding over time
fig_fund_year_cum = ggplot(data = data_fund_year,
                       aes(x = year_funding, y = cumsum(tot_fund))) %>%
  + geom_bar(stat = 'identity', fill = "#3182BD") %>% 
  + geom_text(aes(y = cumsum(tot_fund), label = format(cumsum(tot_fund), big.mark = ",", digits = 1)),
              color = "black", size=2.5, vjust = -0.3) %>%
  + labs(title = "Cumulative evolution of AFD funding related to protected areas",
         subtitle = paste(format(sum(data_fund_year$tot_fund), big.mark = ","), "€ total funding"),
         x = "",
         y = "Funding (€)") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=10, hjust = .5, vjust = .6),
      axis.title.x = element_text(margin = margin(t = 10)),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain'))
fig_fund_year_cum


```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "fig_fund_year.png", sep = "/"),
       plot = fig_fund_year,
       device = "png",
       height = 6, width = 9)
ggsave(paste(tmp, "fig_fund_year_cum.png", sep = "/"),
       plot = fig_fund_year_cum,
       device = "png",
       height = 6, width = 9)


#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/descriptive_stats/funding", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))

```

## Type of funding

Distribution of funding types

```{r}

##Creating dataset
data_type_prod = data_stat_projet_nodupl %>%
  group_by(libelle_produit) %>%
  #number of PAs per funding type
  summarize(n_type = n()) %>%
  ungroup() %>%
  #Frequency of funding types
  mutate(n_pa = sum(n_type),
         freq = round(n_type/n_pa*100, 1),
         libelle_produit = case_when(libelle_produit == "PRETS SOUVERAINS FMI COMPATIBLE" ~ "Prêts souverains FMI-compatible", 
                                     is.na(libelle_produit) ~"Non-renseigné",
                                     TRUE ~ libelle_produit)) %>%
  arrange(desc(libelle_produit)) %>%
  select(-n_pa) %>%
  arrange(-freq)

##Table
# tbl_type_prod = data_type_prod
# names(tbl_type_prod) <- c("Type de financement","Projets", "Proportion (%)")

# print(xtable(tbl_type_prod, type = "latex"),
#       file = "descriptive_stats/funding/tbl_fund_type.tex")

#Pie chart 
pie_type_prod = ggplot(data_type_prod, 
                      aes(x="", y= freq, fill = libelle_produit)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, 
                         label = paste0(round(freq, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  + labs(x = "", y = "",
         title = "Type de financement des projets liées à des aires protégées") %>%
  + scale_fill_brewer(name = "Catégories", palette = "Dark2") %>%
  + theme_void()
pie_type_prod

```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "pie_type_prod.png", sep = "/"),
       plot = pie_type_prod,
       device = "png",
       height = 6, width = 9)

# print(xtable(tbl_type_prod, type = "latex"),
#       file = paste(tmp, "tbl_type_prod.tex", sep = "/"))


#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/descriptive_stats/funding", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```

Average fund by funding type

```{r}

# tbl_fund_avg_type = data_stat_projet_nodupl %>%
#   group_by(libelle_produit) %>%
#   summarize(n_type = n(),
#             tot_fund = sum(mt_fin_global_af_d_prevu_devise)
#             ) %>%
#   mutate(n_pa = sum(n_type),
#          freq_pa = round(n_type/n_pa*100, 1),
#          freq_fund = round(tot_fund/sum(tot_fund)*100, 1),
#          libelle_produit = case_when(libelle_produit == "PRETS SOUVERAINS FMI COMPATIBLE" ~ "Prêts souverains FMI-compatible", TRUE ~ libelle_produit),
#          tot_fund = format(tot_fund, big.mark = " ")) %>%
#   select(c(libelle_produit, n_type, freq_pa, tot_fund, freq_fund)) %>%
#   arrange(-freq_pa) 
# names(tbl_fund_avg_type) = c("Type de financement","Projets", "Proportion d'AP (%)", "Montants (€)", "Proportion des montants (%)")

# print(xtable(tbl_fund_avg_type, type = "latex"),
#       file = "descriptive_stats/funding/tbl_fund_avg_type.tex")

```

## Co-funders

We want to obtain the number of projects co-funded by KFW and FFEM, and the total/average amount given by KFW and FFEM. Unfortunately, for some projects we know KFW or FFEM are co-funder but the amount for the cofunder is not reported in SIOP. Example : ID projet CMR1213.

Thus we only report the number of projects where KFW or FFEM were implied.

```{r}
#Create a table with number of projects funded by FFEM and KfW.

data_fund_cofunder = data_stat_fund %>%
  #Keep one project per line only (for statistics on number !)
  group_by(id_projet) %>%
  slice(1) %>%
  ungroup() %>%
  mutate(cof_short = case_when(grepl("kfw", cofinanciers, ignore.case = TRUE) | grepl("kfw", cofinanciers_siop, ignore.case = TRUE) ~ "KfW",
                               grepl("ffem", cofinanciers, ignore.case = TRUE) | grepl("ffem", cofinanciers_siop, ignore.case = TRUE) ~ "FFEM",
                               TRUE ~ "Other")) %>%
  group_by(cof_short) %>%
  summarise(n = n()) %>%
  ungroup() %>%
  mutate(freq_n = round(n/sum(n)*100, 2),
         ypos_n = cumsum(freq_n) - 0.5*freq_n)

###Figure
fig_cofund_n = ggplot(data = data_fund_cofunder,
                         aes(x = reorder(cof_short, -n), y = n,
                             fill = cof_short)) %>%
  + geom_bar(stat = "identity", width = 0.50, fill="#3182BD") %>%
  + geom_text(aes(label = n, y = n), 
            vjust = -0.2, color="black",
            size=3.5) %>%
  + labs(title = "Number of AFD projects cofunded by KfW or FFEM",
         subtitle = paste("Sample :", sum(data_fund_cofunder$n), "projects"),
         caption = "Other corresponds to projet not co-funded or co-funded by institutions other than FFEM or KfW.",
          x = "", 
          y = "Number") %>%
  + theme(legend.position = "bottom",
      legend.key = element_rect(fill = "white"),
      plot.title = element_text(size = 14, face = "bold"), 
      axis.text.x = element_text(angle = 45,size=9, hjust = .5, vjust = .6),
      panel.background = element_rect(fill = 'white', colour = 'white', 
                                      linewidth = 0.5, linetype = 'solid'),
      panel.grid.major = element_line(colour = 'grey90', linetype = 'solid'),
      panel.grid.minor = element_line(colour = 'grey90', linetype = 'solid'),
      plot.caption = element_text(color = 'grey50', size = 8.5, face = 'plain', hjust = 0))
fig_cofund_n



###Pie

pie_cofund_n = ggplot(data_fund_cofunder, 
                      aes(x="", y= freq_n, fill = cof_short)) %>%
  + geom_bar(width = 1, stat = "identity", color="white") %>%
  + coord_polar("y", start=0) %>%
  + geom_label_repel(aes(x=1.2, label = paste0(round(freq_n, 1), "%")), 
             color = "white", 
             position = position_stack(vjust = 0.55), 
             size=2.5, show.legend = FALSE) %>%
  # + geom_label(aes(x=1.4, label = paste0(freq_iucn, "%")), 
  #              color = "white", 
  #              position = position_stack(vjust = 0.7), size=2.5, 
  #              show.legend = FALSE) %>%
  + labs(title = "Number of AFD projects cofunded by KfW or FFEM",
         subtitle = paste("Sample :", sum(data_fund_cofunder$n), "projects"),
         caption = "Other corresponds to projet not co-funded or co-funded by institutions other than FFEM or KfW.",
          x = "", 
          y = "") %>%
  + scale_fill_brewer(name = "Co-funder", palette = "Dark2") %>%
  + theme_void()
pie_cofund_n
```

```{r, eval = FALSE}
#Saving figures

tmp = paste(tempdir(), "fig", sep = "/")

ggsave(paste(tmp, "fig_cofund_n.png", sep = "/"),
       plot = fig_cofund_n,
       device = "png",
       height = 6, width = 9)

ggsave(paste(tmp, "pie_cofund_n.png", sep = "/"),
       plot = pie_cofund_n,
       device = "png",
       height = 6, width = 9)


#Export to S3 storage

##List of files to save in the temp folder
files <- list.files(tmp, full.names = TRUE)
##Add each file in the bucket (same foler for every file in the temp)
for(f in files) 
  {
  cat("Uploading file", paste0("'", f, "'"), "\n")
  aws.s3::put_object(file = f, 
                     bucket = "projet-afd-eva-ap/descriptive_stats/funding", 
                     region = "", show_progress = TRUE)
  }

#Erase the files in the temp directory

do.call(file.remove, list(list.files(tmp, full.names = TRUE)))
```
